### 2019-04-29 paper.tex
Initial commit

\documentclass[runningheads]{llncs}

\usepackage{graphicx}

\begin{document}

\title{My Cool Title}

\author{Jacobus C. Lock\inst{1} \and
  Gzegorz Cielniak\inst{1} \and
  Andrea Tramontano\inst{2} \and
  Nicola Bellotto\inst{1}
}
\authorrunning{J.C. Lock et. al.}
\institute{University of Lincoln, Lincoln, UK \and
  Universita Degli Studi Di Padova, Italy
}

\maketitle

\begin{abstract}
  Cool abstract here
  \keywords{All the best keywords}
\end{abstract}

\section{Introduction}

It is estimated that there are almost half a billion people today that live with mild to severe levels of vision impairments or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}. There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier. The work we present here is part of the ActiVis project that aims to assist people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera. This system implements ideas from the active vision field~\cite{bajcsy2017,bellotto2013}, but replaces the electro-mechanical servo typically found in active vision systems, with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}. This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.

\begin{figure}
  \centering
  \includegraphics[width=0.38\textwidth]{figures/system_use.png}
  \caption{The system in use during an experiment. }\label{fig:system-in-use}
\end{figure}

\section{Previous Work}

\section{System Design}

\section{Experiment Design}

\section{Results}

\section{Conclusion}

\bibliographystyle{splncs04}
\bibliography{bib}

\end{document}

### 2019-04-29 paper.tex
Final commit before branching off. Also splitting all sentences into their own lines

@@
 \author{Jacobus C. Lock\inst{1} \and
-  Gzegorz Cielniak\inst{1} \and
+  Grzegorz Cielniak\inst{1} \and
   Andrea Tramontano\inst{2} \and
@@
   \centering
-  \includegraphics[width=0.38\textwidth]{figures/system_use.png}
+  \includegraphics[width=0.5\textwidth]{figures/system_use.png}
   \caption{The system in use during an experiment. }\label{fig:system-in-use}
 \end{figure}
+
+Our active search system uses the camera's current and previous views as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to determine the best action to take to reach the target object.
+To enable this, we implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.
 

### 2019-04-29 paper.tex
Added todo command. Added contributions list

@@
 \usepackage{graphicx}
+
+% Package for todo command
+\usepackage{xcolor}
+
+\newcommand\todo[1]{\textcolor{red}{#1}}
 
@@
 Our active search system uses the camera's current and previous views as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to determine the best action to take to reach the target object.
-To enable this, we implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.
+To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.
+
+This work includes the following contributions:
+
+\begin{itemize}
+  \item a POMDP-based human controller that enables object search and guidance on a mobile phone;
+  \item experiments that evaluate the efficacy of the proposed system.
+\end{itemize}
+
+\todo{Add paper layout}
 

### 2019-04-29 paper.tex
Added intial discussion on active vision system

@@
 
-\section{System Design}
+\section{Active Vision System}
+
+The work we present in this paper is an advancement towards the ActiVis projects larger goal of developing a stand-alone mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention.
+This work focuses on guiding a user towards an object in one, static environment and is limited to 2 dimensions (pan and tilt).
+
+A complete system diagram is given in Fig.~\ref{fig:sys-diagram}\todo{cite own work where fig is from if necessary}. 
+This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, but has been modified to incorporate a human within the loop.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.75\textwidth]{figures/control_loop.png}
+  \caption{System control loop: $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
+$K$, $H$ and $P$ are the control, human and sensor blocks respectively.
+}\label{fig:sys-diagram}
+\end{figure}
+
+In this case, the error is defined as the difference between the desired object and the object currently within view. 
+The implication of this modification is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
+However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
+It is therefore important to design \emph{K} to take be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
+These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}
+
+Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector making classification errors that will influence the action that \emph{K} generates.
+In our previous work, we assumed a `perfect classifier' and solved the problem using a plain Markov decision process (MDP). 
+In this work we do away with that somewhat naive assumption and implement a POMDP that can better handle the observation uncertainties inherent to modern object detectors and classifiers. 
+The design of the human controller is discussed next.
 

### 2019-04-30 paper.tex
Added section head
Added experiment design intro@

@@
 
+To evaluate the effectiveness of our POMDP controller and guidance system, we designed a set of experiments that can measure its performance in driving a user towards a target object within the environment.
+We also conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement to compare our results to and provide additional context. 
+This alternative `guidance' system does not actually provide any guidance instructions to the user, instead it provides the user with the raw observation output from the object classifier and makes use of the user's intuition and prior environment knowledge to generate actions.
+The goal of both the guided and unguided experiment cases were to find an object within a static environment. 
+Details on the design of these experiments are given in the next sections.
+
+\subsection{Unguided Case}
+
+\subsection{Guided Case}
+
 \section{Results}

### 2019-04-30 paper.tex
Added unguided experiment section and section on environment design

@@
 \usepackage{graphicx}
+\usepackage{booktabs}
 
@@
 
+The design goal of this experiment is to mimic how a typical person with healthy eyesight would behave if told to look for a given object. 
+In such a scenario, a person would exploit the objects currently within their view and their prior knowledge on a room's typical layout to make a decision on where to look next to find what they are looking for.
+Take for example a person in bathroom facing the basin after washing their hands and looking for a hand-dryer. 
+It is unlikely that a hand dryer would be placed above or below a wash basin so it it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them to find a dryer.
+
+For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object.
+The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
+The app only reads out the objects when the participant requested it to by tapping on the screen. 
+When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.
+
+Each participant was verbally told what the target object was they they were meant to find and each participant was given 45 seconds to find the target object. 
+In this case, the learning effect was ignored in order to mimic the typical search behaviour described earlier. 
+Each experiment run was ended when a target was found or the time limit was reached. 
+This process was repeated a total of 8 times, once for each target object within the environment.
+
 \subsection{Guided Case}
+
+\subsection{Environment Setup}
+
+The environment, and the object placement within it, for both experiments was modelled on a typical office.
+Measures were taken to ensure that both office environments were unique in layout and object placement. 
+However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, since most offices contain the same basic furniture and objects. 
+These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
+All of the objects and their experiment placement is given in Table~\ref{tab:objects}.
+
+\begin{table}
+  \centering
+  \caption{The different objects used within each experiment environment.}\label{tab:objects}
+  \begin{tabular}{p{2cm}cp{0.7cm}c}
+    \toprule
+    & \bf{Guided} & & \bf{Unguided} \\\midrule
+    Door        & X & & X \\\midrule
+    Desk	& X & & X \\\midrule
+    Chair	& X & & X \\\midrule
+    Whiteboard	& X & & X \\\midrule
+    Mouse	& X & & X \\\midrule
+    Monitor	&   & & X \\\midrule
+    Telephone	&   & & X \\\midrule
+    Keyboard	&   & & X \\\midrule
+    Laptop	& X & &   \\\midrule
+    Backpack	& X & &   \\\midrule
+    Mug		& X & &   \\\midrule
+    \bottomrule
+  \end{tabular}
+\end{table}
 

### 2019-04-30 paper.tex
Adde dguided section

@@
 The goal of both the guided and unguided experiment cases were to find an object within a static environment.
+
+We recruited 10 sighted participants that were blindfolded for the experiments, as well as 2 legally blind participants, where 1 was blind from birth and the other suffers from late onset blindness\todo{Give participant stats}.
 Details on the design of these experiments are given in the next sections.
@@
 For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object.
+This process is modelled by the schematic in Fig. MEME\todo{put in figure without controller} where the human, \emph{H}, acts as both the actuator and controller.
 The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
@@
 \subsection{Guided Case}
+
+In this experiment, we evaluate the performance of the guidance system in the object search task, where the perception and control tasks are performed by the guidance system and mobile device and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor.
+This is modelled by the schematic in Fig.~\ref{fig:sys-diagram}.
+
+The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object themselves.
+An experiment run was therefore initiated when the experiment staff selected the target and was terminated when the target object was found or the time limit was exceeded.
+We set a time limit of 45 seconds in this experiment as well.
+Each participant repeated this experiment 8 times, once for each object within the experiment's object set.
 

### 2019-05-03 paper.tex
Added pomdp params and introduction

@@
 
+\section{Human Controller}
+
+The POMDP human control module that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
+It works by generating a trail of virtual waypoints for the user to point the camera towards.
+The waypoint positions are based on the model's pre-trained, internal knowledge on the inter-object spatial relationships and they are placed in a way that maximises the probability of the user pointing to and finding the target object
+A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.
+The design and implementation of this POMDP human controller is discussed here.
+
+\subsection{Design}
+
+A POMDP is an extension to the MDP model that allows it to handle cases where the state is not directly observable, allowing it to be used in more realistic scenarios. 
+In this case, the state is inferred based on the model parameters and the associated sensor accuracy (if a sensor is 100\% accurate, the state would be directly observable).
+The implication of this is that a POMDP-based agent does not know its state at any point in time.
+Instead, a POMDP model can be transformed into a so-called belief MDP\todo{maybe cite} that uses a probabilistic meta belief state that changes with additional observations to reflect the likelihood the agent is in any given state.
+The belief state is fully observable by the agent and can be used to infer the parent POMDP-agent's current state and generate the next action, hence the designation as an MDP.\@
+
+The system uses an object detector and classifier in order to find any objects within the camera's view.
+These detectors and classifiers have some noise associated with them that is caused by misclassifications and similar errors and a POMDP is therefore necessary in this case.
+
+A POMDP model is represented by the 7-tuple
+
+\begin{equation}
+  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \gamma),
+\end{equation}
+
+\noindent where $\mathbf{S}$ represents the agent's state space, $\mathbf{A}$ is a set of actions the agent can execute in any state, $\mathbf{T}$ is a table containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$ after executing action $a$, $a \in \mathbf{A}$ and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a$.
+$\mathbf{\Omega}$ is a set of possible state observations the agent can make, while the table $\mathbf{O}$ contains the probabilities of making state observation $\omego$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
+Finally, the scalar $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
+
+The state and space spaces and the reward and transition functions for this POMDP are the same as the MDP described in~\cite{lock2019active}. 
+The major difference is the addition of an observation matrix that defines the probability of being in any given state after making a new observation.
+In essence, it is a measure of the sensor accuracy, and in this case it describes the object detector's classification accuracy and recall.
+These parameters are given by the following.
+
+\subsubsection{State Space}
+
+The state is given by
+
+\begin{equation}
+  s = \langle z, n, v \rangle,
+\end{equation}
+
+\noindent where $z$ is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
+
+\subsubsection{Actions}
+
+The possible actions an that define the area where the agent will generate the next waypoint are given by
+
+\begin{equation}
+  \mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}
+\end{equation}
+
+\subsubsection{Transitions}
+
+$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\matbf{A}$ from the OpenImages\todo{cite} dataset. 
+For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e.
+UP) the object `keyboard' in 87\% \todo{get real percentage} of images containing both objects.
+The transition function for this case will look like
+
+\begin{equation}
+  \mathbf{T}(s, a, s') = \mathbf{T}(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.87
+\end{equation}
+An example of this relationship can be seen in the image in Fig.~\ref{fig:openimage}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\columnwidth]{figures/desk_example.png}
+  \caption{}\label{fig:openimage}
+\end{figure}
+
+\subsubsection{Reward Function}
+
+The reward function is designed to encourage the agent to find the target object by giving it a substantial reward for doing so, while penalising it for every action it takes that does not results in it finding the target object.
+All of the rewards and when they are given are listed in Table~\ref{tab:rewards}.
+
+\begin{table}
+  \centering
+  \caption{The reward function for the POMDP.\ }\label{tab:rewards}
+  \begin{tabular}{cc}
+    \toprule
+    $r(o = o_{target})$ & 10000 \\ \midrule
+    $r(v = true)$  & -75 \\ \midrule
+    $r(n > n_{\max})$ & -75 \\ \midrule
+    otherwise $r(\cdot)$ & -100  \\ \midrule
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\subsubsection{Observations and Observation Matrix}
+
+The observations the agent can make are identical to the states that the agent can enter. 
+In this case, however, the only uncertainty in the system is introduced by the object detector, since the model can perfectly track the number of steps taken during the search and the locations that waypoints have been generated.
+$\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector. 
+These values were found by performing a set of classifier tests on the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$.
+
+\subsection{Implementation}
+
+\subsubsection{Belief MDP Transformation}
+
+\subsubsection{Training}
+
+\subsubsection{Android App}
+
 \section{Experiment Design}

### 2019-05-03 paper.tex
Fixed syntax issues

@@
 \noindent where $\mathbf{S}$ represents the agent's state space, $\mathbf{A}$ is a set of actions the agent can execute in any state, $\mathbf{T}$ is a table containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$ after executing action $a$, $a \in \mathbf{A}$ and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a$.
-$\mathbf{\Omega}$ is a set of possible state observations the agent can make, while the table $\mathbf{O}$ contains the probabilities of making state observation $\omego$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
+$\mathbf{\Omega}$ is a set of possible state observations the agent can make, while the table $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
 Finally, the scalar $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
@@
 
-$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\matbf{A}$ from the OpenImages\todo{cite} dataset. 
+$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\mathbf{A}$ from the OpenImages\todo{cite} dataset. 
 For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e.

### 2019-05-03 paper.tex
Added discussion on pomdp training

@@
 \usepackage{booktabs}
+\usepackage{amsmath}
 
@@
 The implication of this is that a POMDP-based agent does not know its state at any point in time.
-Instead, a POMDP model can be transformed into a so-called belief MDP\todo{maybe cite} that uses a probabilistic meta belief state that changes with additional observations to reflect the likelihood the agent is in any given state.
+Instead, a POMDP model relies on a so-called belief meta-state that changes with additional observations to reflect the likelihood the agent is in any given state.
 The belief state is fully observable by the agent and can be used to infer the parent POMDP-agent's current state and generate the next action, hence the designation as an MDP.\@
@@
 
-A POMDP model is represented by the 7-tuple
+A POMDP model is represented by the $n$-tuple
 
 \begin{equation}
-  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \gamma),
+  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma),
 \end{equation}
 
-\noindent where $\mathbf{S}$ represents the agent's state space, $\mathbf{A}$ is a set of actions the agent can execute in any state, $\mathbf{T}$ is a table containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$ after executing action $a$, $a \in \mathbf{A}$ and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a$.
+\noindent where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions the agent can execute in any state, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$ after executing action $a$, $a \in \mathbf{A}$ and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a$.
 $\mathbf{\Omega}$ is a set of possible state observations the agent can make, while the table $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
-Finally, the scalar $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
+Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and the scalar $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
+The belief state $\mathbf{b}$ is updated for every timestep and action-observation pair.
+This update is done with
+
+\begin{equation}
+  b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s)
+\end{equation}
 
@@
 
-\noindent where $z$ is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
+\noindent where $z, z\in\mathbf{z}$, is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
 
@@
 The reward function is designed to encourage the agent to find the target object by giving it a substantial reward for doing so, while penalising it for every action it takes that does not results in it finding the target object.
-All of the rewards and when they are given are listed in Table~\ref{tab:rewards}.
+Furthermore, additional penalties are given if the agent generates a waypoint in an area it has explored before $(v = \textrm{true}$) and when it exceeds some search length threshold, denoted by $n_{\max}$.
+All of the rewards and when they are given are summarised by Table~\ref{tab:rewards}.
 
@@
   \centering
-  \caption{The reward function for the POMDP.\ }\label{tab:rewards}
+  \caption{The reward function for the POMDP. }\label{tab:rewards}
   \begin{tabular}{cc}
@@
     $r(o = o_{target})$ & 10000 \\ \midrule
-    $r(v = true)$  & -75 \\ \midrule
+    $r(v = \texrm{true})$  & -75 \\ \midrule
     $r(n > n_{\max})$ & -75 \\ \midrule
@@
 
-\subsubsection{Belief MDP Transformation}
+\subsubsection{Training}
 
-\subsubsection{Training}
+For our system, we encoded a total of 16 objects, including a `nothing' state where the detector does not see anything of interest, into the POMDP and object detector.
+These objects are given by $\mathbf{z}$, defined as
+
+\begin{equation}
+  \begin{split}
+    \mathbf{z} = \{ nothing, monitor, keyboard, mouse, desk, laptop, mug, window,\\ 
+      lamp, backpack, chair, couch, plant, telephone, whiteboard, door \}
+  \end{split}
+\end{equation}
+
+We also set $n_{\max}$ to 12 waypoints, after which the agent gets penalised for every additional waypoint it generates that does not lead to the target object. 
+This results in a total of 352 reachable states ($n_{states} = 16\times11\times2$), with any state containing the target object acting as a terminal state.
+
+The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that an agent can use to produce the optimal waypoint locations.
+This is done by having the agent explore the entire state-action-observation space and optimising the policy to maximise the long-term cumulative reward.
+
+The difficulty of solving POMDPs is that the belief vector is a vector of continuous probability distributions with infinite combinations, making them very time-consuming or even impossible to solve exactly and we found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
+Multiple algorithms that solve POMDPs approximately have been proposed\todo{cite examples} and in this work we used the Point-Based Value Iteration (PBVI) algorithm\todo{cite} to solve the POMDP model
+The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only.
+Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.
 

### 2019-05-04 paper.tex
Starting description of android implementation
Added section on results, figures on time to target

@@
 \usepackage{amsmath}
+\usepackage{subcaption}
+\usepackage{caption}
 
@@
     $r(o = o_{target})$ & 10000 \\ \midrule
-    $r(v = \texrm{true})$  & -75 \\ \midrule
+    $r(v = \textrm{true})$  & -75 \\ \midrule
     $r(n > n_{\max})$ & -75 \\ \midrule
@@
 \subsubsection{Android App}
+
+We made an Android app that implements the object detector and POMDP controller onto a mobile phone that can generate and provide guidance instructions for a user.
 
@@
 
+%\subsection{Target Acquisition}
+
+\subsection{Time to Target}
+
+The time it took a participant to find a target object is an important indicator of performance for the system, where less time indicates a shorter search time and increased performance.
+The data for the search times for each dataset are given in Fig~\ref{fig:boxplot-time}, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
+
+\begin{figure}
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/boxplot_time_to_target.png}
+    \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
+  \end{subfigure}
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/cumplot_time_to_target.png}
+    \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
+  \end{subfigure}
+  \caption{A set of boxplots and CDFs comparing the time it took the participants to find the targets for each experiments. }
+\end{figure}
+
+By inspecting the boxplots in Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the time it took the participants to find the targets on average from 17.8s to 10s per target, ($p = 0.038$).
+This is an average improvement of almost 40\%.
+This is supported by the CDFs in Fig.~\ref{fig:cum-time} that show that \todo{Discuss the less number of objects found and how it is not statistically signioficatn. Perhaps show it in CDF}
+
+\subsection{Movement}
+
+To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
+In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user, enhancing the user experience\todo{maybe cite paper that says less exertion is good}.
+
+The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ dimensions.
+By integrating these data with respect to time, we can get the total displacement for each dimension.
+
 \section{Conclusion}

### 2019-05-04 paper.tex

@@
 \usepackage{amsmath}
-\usepackage{subcaption}
-\usepackage{caption}
 
@@
 \begin{figure}
-  \begin{subfigure}{0.5\textwidth}
   \centering
-    \includegraphics[width=0.9\textwidth]{figures/boxplot_time_to_target.png}
+  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
   \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
-  \end{subfigure}
-  \begin{subfigure}{0.5\textwidth}
+\end{figure}
+\begin{figure}
   \centering
-    \includegraphics[width=0.9\textwidth]{figures/cumplot_time_to_target.png}
+  \includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
   \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
-  \end{subfigure}
-  \caption{A set of boxplots and CDFs comparing the time it took the participants to find the targets for each experiments. }
 \end{figure}

### 2019-05-04 paper.tex
Added section describing audio interface

@@
 
-\subsection{Implementation}
-
 \subsubsection{Training}
@@
 
-\subsubsection{Android App}
+\subsection{Controller Implementation}
 
 We made an Android app that implements the object detector and POMDP controller onto a mobile phone that can generate and provide guidance instructions for a user.  
+This was done by combining an audio interface that can provide non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
+Each of these aspects and their implementation are discussed here.
+
+\subsubsection{Audio Interface}
+
+The target audience of our system are PwVI and we therefore have to provide guidance instructions in a non-visual manner that is intuitive and easy to understand. 
+To avoid blocking a user's access to the ambient sounds (something PwVI typically rely upon extensively), we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.
+
+To describe the waypoints pan and tilt positions, we implemented an improved version of the interface described in~\cite{belloto2013} that exploits a uses a spatialised audio signal.
+However, in this work we only spatialise the audio in the pan dimension only, since our headphones bypass the ear's pinnae that allow a person to determine the tilt angle of a sound source. 
+Instead we exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively\todo{cite} and adjust the sound source's pitch as a function of the waypoint's tilt angle.
+With this interface and set of headphones, we are able to describe the location of a waypoint to a user in 2 dimensions (pan and tilt) in an intuitive an non-intrusive manner.
+
+\subsubsection{Object Detector}
+
+\subsubsection{POMDP Controller}
 

### 2019-05-04 paper.tex
Added section describing the pomdp implementation

@@
 \usepackage{amsmath}
+\usepackage{siunitx}
 
@@
 
+The output from the POMDP model's training process is a policy file that defines the best location to place the next search waypoint based on the device's current state.
+This state is tracked by the device during run-time by recording the device's previous search locations and previous waypoint positions, which is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
+Each grid square represents a \SI{35}{\degree} angular translation, encompassing a \SI{210}{\degree}$times$\SI{210}{\degree} field of view. 
+This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation parameter $o$ is generated by the object detector.
+
+When the user moves the device into a new grid square by rotating the device past \SI{35}{\degree}, thereby making a new $v$ observation and changing the state, or observes a new object, the device triggers the controller to generate a new waypoint location.
+The controller uses the new state observation $\omega$ to update its belief state and queries the policy for the best location to place the new waypoint. 
+The policy output is an action from the action set $\mathbf{A}$ that specifies the next adjacent grid square to place the waypoint.
+For example, an `UP' output would result in the waypoint being placed one grid square, i.e. \SI{35}{\degree}, above where the current grid square within view.
+
 \section{Experiment Design}

### 2019-05-04 paper.tex
Added some references, removed some todos

@@
 The difficulty of solving POMDPs is that the belief vector is a vector of continuous probability distributions with infinite combinations, making them very time-consuming or even impossible to solve exactly and we found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
-Multiple algorithms that solve POMDPs approximately have been proposed\todo{cite examples} and in this work we used the Point-Based Value Iteration (PBVI) algorithm\todo{cite} to solve the POMDP model
+Multiple algorithms that solve POMDPs approximately have been proposed\todo{cite examples} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} to solve the POMDP model.
 The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only.
@@
 
-To describe the waypoints pan and tilt positions, we implemented an improved version of the interface described in~\cite{belloto2013} that exploits a uses a spatialised audio signal.
+To describe the waypoints pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
 However, in this work we only spatialise the audio in the pan dimension only, since our headphones bypass the ear's pinnae that allow a person to determine the tilt angle of a sound source. 
-Instead we exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively\todo{cite} and adjust the sound source's pitch as a function of the waypoint's tilt angle.
+Instead we exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch as a function of the waypoint's tilt angle.
+A similar interface was used in~\cite{schauerte2012assistive}.
 With this interface and set of headphones, we are able to describe the location of a waypoint to a user in 2 dimensions (pan and tilt) in an intuitive an non-intrusive manner.
@@
 This state is tracked by the device during run-time by recording the device's previous search locations and previous waypoint positions, which is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
-Each grid square represents a \SI{35}{\degree} angular translation, encompassing a \SI{210}{\degree}$times$\SI{210}{\degree} field of view. 
+Each grid square represents a \SI{35}{\degree} angular translation, encompassing a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
 This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation parameter $o$ is generated by the object detector.

### 2019-05-05 paper.tex
Added new schematic to experiment section

@@
 For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object.
-This process is modelled by the schematic in Fig. MEME\todo{put in figure without controller} where the human, \emph{H}, acts as both the actuator and controller.
+This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller}, \emph{H}, acts as both the actuator and controller.
 The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
@@
 When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/control_loop_no_controller.png}
+  \caption{A set of CDFs comparing the time to target. }\label{fig:sys-diagram-no-controller}
+\end{figure}
 
@@
 \end{figure}
+
 \begin{figure}

### 2019-05-05 paper.tex
Need to  replace into picture, added contribution

--- 2019-05-04 paper.tex
@@
 \usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{siunitx}
 
@@
 The work we present here is part of the ActiVis project that aims to assist people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
-This system implements ideas from the active vision field~\cite{bajcsy2017,bellotto2013}, but replaces the electro-mechanical servo typically found in active vision systems, with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
+This system implements ideas from the active vision field~\cite{bajcsy2017,bellotto2013}, but replaces the electro-mechanical servo typically found in active vision systems, with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}\todo{replace with actual picture}.
 This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.
@@
   \item a POMDP-based human controller that enables object search and guidance on a mobile phone;
+  \item a complete system pipeline that includes guidance instruction generation and transmission;
   \item experiments that evaluate the efficacy of the proposed system.
@@
 
-\section{Active Vision System}
-
-The work we present in this paper is an advancement towards the ActiVis projects larger goal of developing a stand-alone mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention.
-This work focuses on guiding a user towards an object in one, static environment and is limited to 2 dimensions (pan and tilt).
-
-A complete system diagram is given in Fig.~\ref{fig:sys-diagram}\todo{cite own work where fig is from if necessary}. 
-This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, but has been modified to incorporate a human within the loop.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.75\textwidth]{figures/control_loop.png}
-  \caption{System control loop: $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
-$K$, $H$ and $P$ are the control, human and sensor blocks respectively.
-}\label{fig:sys-diagram}
-\end{figure}
-
-In this case, the error is defined as the difference between the desired object and the object currently within view. 
-The implication of this modification is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
-However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
-It is therefore important to design \emph{K} to take be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
-These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}
-
-Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector making classification errors that will influence the action that \emph{K} generates.
-In our previous work, we assumed a `perfect classifier' and solved the problem using a plain Markov decision process (MDP). 
-In this work we do away with that somewhat naive assumption and implement a POMDP that can better handle the observation uncertainties inherent to modern object detectors and classifiers. 
-The design of the human controller is discussed next.
-
-\section{Human Controller}
-
-The POMDP human control module that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
-It works by generating a trail of virtual waypoints for the user to point the camera towards.
-The waypoint positions are based on the model's pre-trained, internal knowledge on the inter-object spatial relationships and they are placed in a way that maximises the probability of the user pointing to and finding the target object
-A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.
-The design and implementation of this POMDP human controller is discussed here.
-
-\subsection{Design}
-
-A POMDP is an extension to the MDP model that allows it to handle cases where the state is not directly observable, allowing it to be used in more realistic scenarios. 
-In this case, the state is inferred based on the model parameters and the associated sensor accuracy (if a sensor is 100\% accurate, the state would be directly observable).
-The implication of this is that a POMDP-based agent does not know its state at any point in time.
-Instead, a POMDP model relies on a so-called belief meta-state that changes with additional observations to reflect the likelihood the agent is in any given state.
-The belief state is fully observable by the agent and can be used to infer the parent POMDP-agent's current state and generate the next action, hence the designation as an MDP.\@
-
-The system uses an object detector and classifier in order to find any objects within the camera's view.
-These detectors and classifiers have some noise associated with them that is caused by misclassifications and similar errors and a POMDP is therefore necessary in this case.
-
-A POMDP model is represented by the $n$-tuple
-
-\begin{equation}
-  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma),
-\end{equation}
-
-\noindent where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions the agent can execute in any state, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$ after executing action $a$, $a \in \mathbf{A}$ and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a$.
-$\mathbf{\Omega}$ is a set of possible state observations the agent can make, while the table $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
-Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and the scalar $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
-The belief state $\mathbf{b}$ is updated for every timestep and action-observation pair.
-This update is done with
-
-\begin{equation}
-  b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s)
-\end{equation}
-
-The state and space spaces and the reward and transition functions for this POMDP are the same as the MDP described in~\cite{lock2019active}. 
-The major difference is the addition of an observation matrix that defines the probability of being in any given state after making a new observation.
-In essence, it is a measure of the sensor accuracy, and in this case it describes the object detector's classification accuracy and recall.
-These parameters are given by the following.
-
-\subsubsection{State Space}
-
-The state is given by
-
-\begin{equation}
-  s = \langle z, n, v \rangle,
-\end{equation}
-
-\noindent where $z, z\in\mathbf{z}$, is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
-
-\subsubsection{Actions}
-
-The possible actions an that define the area where the agent will generate the next waypoint are given by
-
-\begin{equation}
-  \mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}
-\end{equation}
-
-\subsubsection{Transitions}
-
-$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\mathbf{A}$ from the OpenImages\todo{cite} dataset. 
-For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e.
-UP) the object `keyboard' in 87\% \todo{get real percentage} of images containing both objects.
-The transition function for this case will look like
-
-\begin{equation}
-  \mathbf{T}(s, a, s') = \mathbf{T}(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.87
-\end{equation}
-An example of this relationship can be seen in the image in Fig.~\ref{fig:openimage}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\columnwidth]{figures/desk_example.png}
-  \caption{}\label{fig:openimage}
-\end{figure}
-
-\subsubsection{Reward Function}
-
-The reward function is designed to encourage the agent to find the target object by giving it a substantial reward for doing so, while penalising it for every action it takes that does not results in it finding the target object.
-Furthermore, additional penalties are given if the agent generates a waypoint in an area it has explored before $(v = \textrm{true}$) and when it exceeds some search length threshold, denoted by $n_{\max}$.
-All of the rewards and when they are given are summarised by Table~\ref{tab:rewards}.
-
-\begin{table}
-  \centering
-  \caption{The reward function for the POMDP. }\label{tab:rewards}
-  \begin{tabular}{cc}
-    \toprule
-    $r(o = o_{target})$ & 10000 \\ \midrule
-    $r(v = \textrm{true})$  & -75 \\ \midrule
-    $r(n > n_{\max})$ & -75 \\ \midrule
-    otherwise $r(\cdot)$ & -100  \\ \midrule
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsubsection{Observations and Observation Matrix}
-
-The observations the agent can make are identical to the states that the agent can enter. 
-In this case, however, the only uncertainty in the system is introduced by the object detector, since the model can perfectly track the number of steps taken during the search and the locations that waypoints have been generated.
-$\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector. 
-These values were found by performing a set of classifier tests on the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$.
-
-\subsubsection{Training}
-
-For our system, we encoded a total of 16 objects, including a `nothing' state where the detector does not see anything of interest, into the POMDP and object detector.
-These objects are given by $\mathbf{z}$, defined as
-
-\begin{equation}
-  \begin{split}
-    \mathbf{z} = \{ nothing, monitor, keyboard, mouse, desk, laptop, mug, window,\\ 
-      lamp, backpack, chair, couch, plant, telephone, whiteboard, door \}
-  \end{split}
-\end{equation}
-
-We also set $n_{\max}$ to 12 waypoints, after which the agent gets penalised for every additional waypoint it generates that does not lead to the target object. 
-This results in a total of 352 reachable states ($n_{states} = 16\times11\times2$), with any state containing the target object acting as a terminal state.
-
-The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that an agent can use to produce the optimal waypoint locations.
-This is done by having the agent explore the entire state-action-observation space and optimising the policy to maximise the long-term cumulative reward.
-
-The difficulty of solving POMDPs is that the belief vector is a vector of continuous probability distributions with infinite combinations, making them very time-consuming or even impossible to solve exactly and we found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
-Multiple algorithms that solve POMDPs approximately have been proposed\todo{cite examples} and in this work we used the Point-Based Value Iteration (PBVI) algorithm\todo{cite} to solve the POMDP model
-The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only.
-Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.
-
-\subsection{Controller Implementation}
-
-We made an Android app that implements the object detector and POMDP controller onto a mobile phone that can generate and provide guidance instructions for a user.  
-This was done by combining an audio interface that can provide non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
-Each of these aspects and their implementation are discussed here.
-
-\subsubsection{Audio Interface}
-
-The target audience of our system are PwVI and we therefore have to provide guidance instructions in a non-visual manner that is intuitive and easy to understand. 
-To avoid blocking a user's access to the ambient sounds (something PwVI typically rely upon extensively), we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.
-
-To describe the waypoints pan and tilt positions, we implemented an improved version of the interface described in~\cite{belloto2013} that exploits a uses a spatialised audio signal.
-However, in this work we only spatialise the audio in the pan dimension only, since our headphones bypass the ear's pinnae that allow a person to determine the tilt angle of a sound source. 
-Instead we exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively\todo{cite} and adjust the sound source's pitch as a function of the waypoint's tilt angle.
-With this interface and set of headphones, we are able to describe the location of a waypoint to a user in 2 dimensions (pan and tilt) in an intuitive an non-intrusive manner.
-
-\subsubsection{Object Detector}
-
-\subsubsection{POMDP Controller}
-
-The output from the POMDP model's training process is a policy file that defines the best location to place the next search waypoint based on the device's current state.
-This state is tracked by the device during run-time by recording the device's previous search locations and previous waypoint positions, which is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
-Each grid square represents a \SI{35}{\degree} angular translation, encompassing a \SI{210}{\degree}$times$\SI{210}{\degree} field of view. 
-This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation parameter $o$ is generated by the object detector.
-
-When the user moves the device into a new grid square by rotating the device past \SI{35}{\degree}, thereby making a new $v$ observation and changing the state, or observes a new object, the device triggers the controller to generate a new waypoint location.
-The controller uses the new state observation $\omega$ to update its belief state and queries the policy for the best location to place the new waypoint. 
-The policy output is an action from the action set $\mathbf{A}$ that specifies the next adjacent grid square to place the waypoint.
-For example, an `UP' output would result in the waypoint being placed one grid square, i.e. \SI{35}{\degree}, above where the current grid square within view.
+\section{System Design}
 
@@
 
-To evaluate the effectiveness of our POMDP controller and guidance system, we designed a set of experiments that can measure its performance in driving a user towards a target object within the environment.
-We also conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement to compare our results to and provide additional context. 
-This alternative `guidance' system does not actually provide any guidance instructions to the user, instead it provides the user with the raw observation output from the object classifier and makes use of the user's intuition and prior environment knowledge to generate actions.
-The goal of both the guided and unguided experiment cases were to find an object within a static environment.
-
-We recruited 10 sighted participants that were blindfolded for the experiments, as well as 2 legally blind participants, where 1 was blind from birth and the other suffers from late onset blindness\todo{Give participant stats}.
-Details on the design of these experiments are given in the next sections.
-
-\subsection{Unguided Case}
-
-The design goal of this experiment is to mimic how a typical person with healthy eyesight would behave if told to look for a given object. 
-In such a scenario, a person would exploit the objects currently within their view and their prior knowledge on a room's typical layout to make a decision on where to look next to find what they are looking for.
-Take for example a person in bathroom facing the basin after washing their hands and looking for a hand-dryer. 
-It is unlikely that a hand dryer would be placed above or below a wash basin so it it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them to find a dryer.
-
-For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object.
-This process is modelled by the schematic in Fig. MEME\todo{put in figure without controller} where the human, \emph{H}, acts as both the actuator and controller.
-The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
-The app only reads out the objects when the participant requested it to by tapping on the screen. 
-When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.
-
-Each participant was verbally told what the target object was they they were meant to find and each participant was given 45 seconds to find the target object. 
-In this case, the learning effect was ignored in order to mimic the typical search behaviour described earlier. 
-Each experiment run was ended when a target was found or the time limit was reached. 
-This process was repeated a total of 8 times, once for each target object within the environment.
-
-\subsection{Guided Case}
-
-In this experiment, we evaluate the performance of the guidance system in the object search task, where the perception and control tasks are performed by the guidance system and mobile device and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor.
-This is modelled by the schematic in Fig.~\ref{fig:sys-diagram}.
-
-The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object themselves.
-An experiment run was therefore initiated when the experiment staff selected the target and was terminated when the target object was found or the time limit was exceeded.
-We set a time limit of 45 seconds in this experiment as well.
-Each participant repeated this experiment 8 times, once for each object within the experiment's object set.
-
-\subsection{Environment Setup}
-
-The environment, and the object placement within it, for both experiments was modelled on a typical office.
-Measures were taken to ensure that both office environments were unique in layout and object placement. 
-However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, since most offices contain the same basic furniture and objects. 
-These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
-All of the objects and their experiment placement is given in Table~\ref{tab:objects}.
-
-\begin{table}
-  \centering
-  \caption{The different objects used within each experiment environment.}\label{tab:objects}
-  \begin{tabular}{p{2cm}cp{0.7cm}c}
-    \toprule
-    & \bf{Guided} & & \bf{Unguided} \\\midrule
-    Door        & X & & X \\\midrule
-    Desk	& X & & X \\\midrule
-    Chair	& X & & X \\\midrule
-    Whiteboard	& X & & X \\\midrule
-    Mouse	& X & & X \\\midrule
-    Monitor	&   & & X \\\midrule
-    Telephone	&   & & X \\\midrule
-    Keyboard	&   & & X \\\midrule
-    Laptop	& X & &   \\\midrule
-    Backpack	& X & &   \\\midrule
-    Mug		& X & &   \\\midrule
-    \bottomrule
-  \end{tabular}
-\end{table}
-
 \section{Results}
-
-%\subsection{Target Acquisition}
-
-\subsection{Time to Target}
-
-The time it took a participant to find a target object is an important indicator of performance for the system, where less time indicates a shorter search time and increased performance.
-The data for the search times for each dataset are given in Fig~\ref{fig:boxplot-time}, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
-  \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
-\end{figure}
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
-  \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
-\end{figure}
-
-By inspecting the boxplots in Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the time it took the participants to find the targets on average from 17.8s to 10s per target, ($p = 0.038$).
-This is an average improvement of almost 40\%.
-This is supported by the CDFs in Fig.~\ref{fig:cum-time} that show that \todo{Discuss the less number of objects found and how it is not statistically signioficatn. Perhaps show it in CDF}
-
-\subsection{Movement}
-
-To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
-In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user, enhancing the user experience\todo{maybe cite paper that says less exertion is good}.
-
-The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ dimensions.
-By integrating these data with respect to time, we can get the total displacement for each dimension.
 

### 2019-05-05 paper.tex
Added paper layout to intro and section labels

@@
 
-\todo{Add paper layout}
+Section~\ref{sec:previous-work} discusses relevant work that has already been done, followed by a description of the active vision system and human controller in Sections~\ref{sec:active-vision} and~\ref{sec:human-controller} respectively.
+The experiments that were conducted in this work, and their results, are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.
 
-\section{Previous Work}
+\section{Previous Work}\label{sec:previous-work}
 
-\section{Active Vision System}
+\section{Active Vision System}\label{sec:active-vision}
 
@@
 
-\section{Human Controller}
+\section{Human Controller}\label{sec:human-controller}
 
@@
 
-\section{Experiment Design}
+\section{Experiment Design}\label{sec:experiments}
 
@@
 
-\section{Results}
-
-%\subsection{Target Acquisition}
+\section{Results}\label{sec:results}
 
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec:conclusion}
 

### 2019-05-05 paper.tex
Added sections on previous work, added more references to bib

@@
 \section{Previous Work}\label{sec:previous-work}
+
+Making a mobile device that can detect objects and guide a PwVI in real-time and using on-board processing power has become much more feasible in recent years, thanks to improvements to mobile computing power and image processing methods.
+Early attempts to solve this guidance problem made use of special markers or barcodes, encoded with object or environmental information, and a smartphone that can efficiently scan the environment for these simple patterns~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}.
+The device then uses some feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
+Improvements to feature detectors and deep networks have made it more viable~\cite{redmon2016you,huang2017speed} to replace the markers with real objects, while providing the same guidance functionality.
+The SIFT and SURF-based systems in~\cite{schauerte2012assistive} is an example of a markerless system.
+An alternative detection approach proposed in~\cite{bigham2010vizwiz}, and commercialised in the `Be My Eyes' app~\cite{bemyeyes2019}, requires the user to send a photo of their environment and target object to a Mechanical Turk worker or volunteer that then sends the position of the requested object within the picture back to the user.
+
+The issue with the marker-based approach is that it requires a significant amount of effort to place and maintain markers around an environment.
+This problem is remedied in the markerless systems.
+However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves first before any guidance can be provided.
+The human-based systems from~\cite{bigham2010vizwiz,bemyeyes2019} can leverage a human's understanding of the environment to help guide a person to the correct area, but the drawback here is that there is a significant lag time and a significant reliance on a good internet connection and remote worker being available.
+Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing a controller that provides the user with instructions on where to point the device to find an out of view object and we proved that this is a viable method to search for an object.
+However, this work relied upon physical barcodes, encoded with object information, to simulate real objects.
+In this work, we are replacing the barcodes with real objects, thereby closing the object detection and guidance loop.
+
+\todo{Object detectors}
 

### 2019-05-05 paper.tex
Removed a few todos

@@
 
-A complete system diagram is given in Fig.~\ref{fig:sys-diagram}\todo{cite own work where fig is from if necessary}. 
+A complete system diagram is given in Fig.~\ref{fig:sys-diagram}. 
 This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, but has been modified to incorporate a human within the loop.
@@
 It is therefore important to design \emph{K} to take be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
-These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}
+%These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}
 

### 2019-05-05 paper.tex
Added new bib entries and listed POMDP algorithms

@@
 The difficulty of solving POMDPs is that the belief vector is a vector of continuous probability distributions with infinite combinations, making them very time-consuming or even impossible to solve exactly and we found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
-Multiple algorithms that solve POMDPs approximately have been proposed\todo{cite examples} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} to solve the POMDP model.
+Multiple algorithms that solve POMDPs approximately have been proposed~\cite{bargiacchi2016dynamic,kaelbling1998planning,silver2010monte,spaan2005perseus} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library~\cite{aitoolbox} to solve the POMDP model.
 The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only.

### 2019-05-05 paper.tex
Removed table of items per room and put it in normal list

@@
 These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
-All of the objects and their experiment placement is given in Table~\ref{tab:objects}.
+The objects in the guided experiment environment is
 
-\begin{table}
+\begin{equation}
+  z_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
+\end{equation}
+while the objects in the unguided experiment are
+
+\begin{equation}
+  z_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
+\end{equation}
+A picture of the unguided experiment environment is given in Fig.~\ref{fig:experiment-env}.
+
+\begin{figure}
   \centering
-  \caption{The different objects used within each experiment environment.}\label{tab:objects}
-  \begin{tabular}{p{2cm}cp{0.7cm}c}
-    \toprule
-    & \bf{Guided} & & \bf{Unguided} \\\midrule
-    Door        & X & & X \\\midrule
-    Desk	& X & & X \\\midrule
-    Chair	& X & & X \\\midrule
-    Whiteboard	& X & & X \\\midrule
-    Mouse	& X & & X \\\midrule
-    Monitor	&   & & X \\\midrule
-    Telephone	&   & & X \\\midrule
-    Keyboard	&   & & X \\\midrule
-    Laptop	& X & &   \\\midrule
-    Backpack	& X & &   \\\midrule
-    Mug		& X & &   \\\midrule
-    \bottomrule
-  \end{tabular}
-\end{table}
+  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
+  \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
+\end{figure}
 
@@
 
-The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ dimensions.
+The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ (tilt) dimensions.
 By integrating these data with respect to time, we can get the total displacement for each dimension.

### 2019-05-05 paper.tex
Added keywords, added openimage reference and real percentage for monitor/keyboard relatoonship

@@
   Cool abstract here
-  \keywords{All the best keywords}
+  \keywords{Active vision, vision impairment, object detection}
 \end{abstract}
@@
 \begin{equation}
-  b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s)
+  b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s), 
 \end{equation}
+where $\eta$ is a normalisation factor.
 
@@
 
-$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\mathbf{A}$ from the OpenImages\todo{cite} dataset. 
+$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\mathbf{A}$ from the OpenImages~\cite{openimages} dataset. 
 For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e.
-UP) the object `keyboard' in 87\% \todo{get real percentage} of images containing both objects.
+UP) the object `keyboard' in 16\% of images containing both objects.
 The transition function for this case will look like
@@
 \begin{equation}
-  \mathbf{T}(s, a, s') = \mathbf{T}(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.87
+  \mathbf{T}(s, a, s') = \mathbf{T}(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16.
 \end{equation}
@@
   \includegraphics[width=0.5\columnwidth]{figures/desk_example.png}
-  \caption{}\label{fig:openimage}
+  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects}\label{fig:openimage}
 \end{figure}

### 2019-05-05 paper.tex
Changed picture caption
Adding abstract

@@
 \begin{abstract}
-  Cool abstract here
+  The ActiVis project aims to deliver a system for a mobile device that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
+  To do so, it uses new developments in object detection methods, mobile computing and action generation. 
   \keywords{Active vision, vision impairment, object detection}
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/control_loop_no_controller.png}
-  \caption{A set of CDFs comparing the time to target. }\label{fig:sys-diagram-no-controller}
+  \includegraphics[width=0.5\textwidth]{figures/control_loop_no_controller.png}
+  \caption{The control loop with the human acting as bot manipulator and controller. }\label{fig:sys-diagram-no-controller}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
-  \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
+  \includegraphics[width=0.7\textwidth]{figures/environment.png}
+  \caption{A picture of the experiment setup. }\label{fig:boxplot-time}
 \end{figure}

### 2019-05-05 paper.tex
Added previous work for object detector. Need to add references

@@
 
-\todo{Object detectors}
+Object detectors can be divided into two main categories that use single-stage and 2-stage methods.  
+The two-stage methods use a region proposal approach [ref] where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
+They typically reach higher accuracy, but at the cost of more memory and computational resources.\todo{cite}
+The Faster-RCNN [ref] is an example of a 2-stage network that uses RPN\todo{what is rpn} for region proposals. 
+On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
+These methods, such as Single-Shot Detection (SSD) and You Only Look Once (YOLO), typically need less computational resources, but at the cost of lower accuracy.\todo{cite} 
+Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
+There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
+Mobilenet [ref] is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
+This leads to model that uses much less memory, but with a small drop in accuracy\todo{cite}.
 
@@
 
+The SSD-Lite network is a single-stage object detection network that is based on the SSD architecture, but uses MobileNetV2\todo{cite} for its backbone.
+This leads to a more `lightweight' model that has less parameters and requires less memory to perform inference tasks, which makes it suitable for a mobile platform.
+
 \subsubsection{POMDP Controller}

### 2019-05-05 paper.tex
Started adding object detector description and references

--- 2019-05-05 paper.tex
@@
 
-\todo{Object detectors}
+Object detectors can be divided into two main categories that use single-stage and 2-stage methods.  
+The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects.
+They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements.\todo{cite}
+On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
+These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
+Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
+There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
+MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
+This leads to model that uses much less memory, but again with a small drop in accuracy.
 
@@
 
+The SSD-Lite network is a single-stage object detection network that is based on the SSD architecture, but uses MobileNetV2\todo{cite} for its backbone.
+This leads to a more `lightweight' model that has less parameters and requires less memory to perform inference tasks, which makes it suitable for a mobile platform. 
+This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
+When compared with the full SSD model, it achieves a slightly lower mAPs (0.25), but with significantly less parameters (34.3M) and FLOPS (34.36B).
+\todo{compare with alterniative}
+
 \subsubsection{POMDP Controller}

### 2019-05-06 paper.tex
Adding more detail to object detector section and comparing it to others sstems

@@
 \begin{equation}
-  s = \langle z, n, v \rangle,
+  s = \langle u, n, v \rangle,
 \end{equation}
 
-\noindent where $z, z\in\mathbf{z}$, is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
+\noindent where $u, u\in\mathbf{U}$, is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
 
@@
 For our system, we encoded a total of 16 objects, including a `nothing' state where the detector does not see anything of interest, into the POMDP and object detector.
-These objects are given by $\mathbf{z}$, defined as
+These objects are given by $\mathbf{U}$, defined as
 
@@
   \begin{split}
-    \mathbf{z} = \{ nothing, monitor, keyboard, mouse, desk, laptop, mug, window,\\ 
+    \mathbf{U} = \{ nothing, monitor, keyboard, mouse, desk, laptop, mug, window,\\ 
       lamp, backpack, chair, couch, plant, telephone, whiteboard, door \}
@@
 
-The SSD-Lite network is a single-stage object detection network that is based on the SSD architecture, but uses MobileNetV2\todo{cite} for its backbone.
+The SSD-Lite network is a single-stage object detection network that is based on the SSD architecture, but uses MobileNetV2~\cite{sandler2018mobilenetv2} for its backbone.
 This leads to a more `lightweight' model that has less parameters and requires less memory to perform inference tasks, which makes it suitable for a mobile platform. 
@@
 When compared with the full SSD model, it achieves a slightly lower mAPs (0.25), but with significantly less parameters (34.3M) and FLOPS (34.36B).
-\todo{compare with alterniative}
+Tiny-DSOD~\cite{li2018tinydsod} is another object detection network focussed on mobile compatibility that is an alternative to the SSD-Lite network with similar accuracy and computing requirements(mAPs$=0.23$, parameters$=$1.15M, FLOPS$=$1.12B).
+However, we found that the SSD-Lite version produced better results in this application and we chose to implement it into our system.
+
+The network was trained with a maximum of 10000 annotated images for each object class in $\mathbf{A}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
+The images were taken from the OpenImages~\cite{openimages} dataset.
+We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
+This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
+\todo{add mAPs we achived}
 
@@
 \begin{equation}
-  z_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
+  u_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
 \end{equation}
@@
 \begin{equation}
-  z_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
+  u_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
 \end{equation}

### 2019-05-06 paper.tex
Added more to abstract

@@
   The ActiVis project aims to deliver a system for a mobile device that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
-  To do so, it uses new developments in object detection methods, mobile computing and action generation. 
+  To do so, it uses new developments in object detection methods, mobile computing, action generation and human-computer interfacing to interpret the user's surroundings and present useful guidance directions.
+  Our approach to action generation used a Markov Decision Process (MDP) to track the system's state and output the next best location to investigate to find a target object and has been shown to work in principle in~\cite{lock2019active}.
+  This work expands upon that by adding an object detector and adapting the decision-making process accordingly, providing a complete object search and guidance pipeline.
+  The improved ActiVis system was evaluated in a set of experiments and it outperformed the baseline, unguided case.
   \keywords{Active vision, vision impairment, object detection}
@@
   \includegraphics[width=0.7\textwidth]{figures/environment.png}
-  \caption{A picture of the experiment setup. }\label{fig:boxplot-time}
+  \caption{A picture of the experiment setup. }\label{fig:experiment-env}
 \end{figure}

### 2019-05-06 paper.tex
Added discussions on results and added figures

@@
 
+\subsection{Target Acquisition}
+
+The target acquisition rate (TAR) is the proportion of experiment runs where the participant successfully found the target object with each respective system. 
+For example, a TAR of 0.5 indicates that a participant found the target objects 50\% of searches. 
+We set an upper time limit for each object search run of 45 seconds.
+When this upper threshold was reached, the search was recorded as a failure and the next run was started.
+
+We found that the unguided case produced a higher average TAR than the guided case (0.54 vs.
+0.46), meaning that a participant was more around 8\% more likely to find more objects without our guidance than with it.
+However, the Kruskal-Wallis test for non-normal data shows that these sets of results are not statistically significantly different from one another ($p = 0.16$), meaning we are unable to conclude which approach produced better results.
+The results are summarised in Table~\ref{tab:results}.
+
+\begin{table}
+  \centering
+  \caption{A summary of the results. }\label{tab:results}
+  \begin{tabular}{ccccc}
+    \toprule
+     & avg & std & avg &std \\ \midrule
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 \subsection{Time to Target}
 
+\todo{Should I add CDF?}
 The time it took a participant to find a target object is an important indicator of performance for the system, where less time indicates a shorter search time and increased performance.
-The data for the search times for each dataset are given in Fig~\ref{fig:boxplot-time}, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
+The data for the search times for each dataset are given in Fig~\ref{fig:boxplot-time}.%, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
-  \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
+  %\caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
+%\end{figure}
 
-By inspecting the boxplots in Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the time it took the participants to find the targets on average from 17.8s to 10s per target, ($p = 0.038$).
-This is an average improvement of almost 40\%.
-This is supported by the CDFs in Fig.~\ref{fig:cum-time} that show that \todo{Discuss the less number of objects found and how it is not statistically signioficatn. Perhaps show it in CDF}
+\todo{update numbers}
+%To compensate for the different numbers of targets found per participant and for each experiment setup, we average each participant's results, giving us 10 samples per experiment. 
+By inspecting the boxplots in Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
+This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p=0.045$).
+These results are summarised in Table~\ref{tab:results}. 
+With this 27\% reduction in total time spent searching for a target object, we can conclude that a user benefits from using our smart guidance system, as opposed to relying on a simple object reader. 
+%This is supported by the CDFs in Fig.~\ref{fig:cum-time} that show that \todo{Discuss the less number of objects found and how it is not statistically signioficatn. Perhaps show it in CDF}
 
@@
 The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ (tilt) dimensions.
-By integrating these data with respect to time, we can get the total displacement for each dimension.
+By integrating these data we can obtain and compare the total absolute displacement for each dimension.
+The angle and distance results are plotted in the boxplots in Figs.~\ref{fig:boxplot-angle} and~\ref{fig:boxplot-dist} respectively.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/boxplot_angle.png}
+  \caption{A set of boxplots comparing the angular distance the device travelled for each experiment. }\label{fig:boxplot-angle}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/boxplot_dist.png}
+  \caption{A set of boxplots comparing the distance the device travelled for each experiment. }\label{fig:boxplot-dist}
+\end{figure}
+
+The boxplots for the total angle displacement show a consistent reduction in radians for the guided case for both the pan (\SI{0.68}{\radian} vs.
+\SI{0.99}{\radian}, $p=0.029$) and tilt dimensions (\SI{0.68}{\radian} vs.
+\SI{1.05}{\radian}, $p=0.011$).
+The guidance system therefore reduces the total angular displacement to find the objects by 31\% and 35\% for the pan and tilt dimensions respectively. 
+The total linear displacement is also reduced when using the guidance interface by approximately 36\% (\SI{0.23}{\metre} vs. \SI{0.36}{\metre}, $p=0.012$).
+These results are summarised in Table~\ref{tab:results}.
+To conclude, the data show that the guidance interface reduced the total angular and linear displacement required to find the target objects in all dimensions by at least 31\%, reducing the total effort required by the user.
 

### 2019-05-06 paper.tex
Added conclusion

@@
 
+In this work, we present a mobile guidance system that uses an object detector to scan the environment for objects and a POMDP-based controller and audio interface to present the user with guidance instructions.
+We implemented this system into an Android app and tested it with a group of 10 participants to evaluate its effectiveness compared to a baseline, unguided case that only uses the object detector and relies on the human to generate their own search path.
+The key results from these experiment is that the guidance system improved the participants' target-finding performance, reducing the search time and overall camera manipulation effort required.
+However, the participants were able to find 8\% more objects on average in the unguided case, but this result was found to be statistically insignificant.
+
+The next steps for the project are to refine and expand the object detector to include objects from other environments.
+
 \bibliographystyle{splncs04}

### 2019-05-06 paper.tex
Added new reference, took care of todos

@@
 
-\title{My Cool Title}
+\title{ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments}
 
@@
   Grzegorz Cielniak\inst{1} \and
-  Andrea Tramontano\inst{2} \and
+  Andrea G. Tramontano\inst{2} \and
   Nicola Bellotto\inst{1}
 }
-\authorrunning{J.C. Lock et. al.}
+\authorrunning{Jacobus C. Lock et. al.}
 \institute{University of Lincoln, Lincoln, UK \and
@@
 The work we present here is part of the ActiVis project that aims to assist people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
-This system implements ideas from the active vision field~\cite{bajcsy2017,bellotto2013}, but replaces the electro-mechanical servo typically found in active vision systems, with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}\todo{replace with actual picture}.
+This system implements ideas from the active vision field~\cite{bajcsy2017,bellotto2013}, but replaces the electro-mechanical servo typically found in active vision systems, with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
 This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.
@@
   \includegraphics[width=0.5\textwidth]{figures/system_use.png}
-  \caption{The system in use during an experiment. }\label{fig:system-in-use}
+  \caption{The system in use during an experiment with a blindfolded participant. }\label{fig:system-in-use}
 \end{figure}
@@
 To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.
-
-This work includes the following contributions:
+This work makes the following contributions:
 
@@
 The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects.
-They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements.\todo{cite}
+They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
 On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
@@
   \includegraphics[width=0.75\textwidth]{figures/control_loop.png}
-  \caption{System control loop: $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
-$K$, $H$ and $P$ are the control, human and sensor blocks respectively.
-}\label{fig:sys-diagram}
+  \caption{The system control loop including a human and the controller.}\label{fig:sys-diagram}
 \end{figure}
@@
 
-The network was trained with a maximum of 10000 annotated images for each object class in $\mathbf{A}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
+The network was trained with a maximum of 10000 annotated object samples for each object class in $\mathbf{A}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
 The images were taken from the OpenImages~\cite{openimages} dataset.
-We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
-This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
-\todo{add mAPs we achived}
+We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
+With 120 training epochs with 1000 iterations each, we achieved a mAPs of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android. 
+%We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
+%This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
+%\todo{add mAPs we achived}
 
@@
 
-We recruited 10 sighted participants that were blindfolded for the experiments, as well as 2 legally blind participants, where 1 was blind from birth and the other suffers from late onset blindness\todo{Give participant stats}.
+We recruited 10 participants (8 male, 2 female; average age 24.2 years) for the experiments, including 2 legally blind participants, where 1 was blind from birth and the other suffers from late onset blindness.
 Details on the design of these experiments are given in the next sections.
@@
 \end{equation}
-A picture of the unguided experiment environment is given in Fig.~\ref{fig:experiment-env}.
+%A picture of the unguided experiment environment is given in Fig.~\ref{fig:experiment-env}.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{figures/environment.png}
-  \caption{A picture of the experiment setup. }\label{fig:experiment-env}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.7\textwidth]{figures/environment.png}
+  %\caption{A picture of the experiment setup. }\label{fig:experiment-env}
+%\end{figure}
 
@@
 
-\todo{Should I add CDF?}
+%\todo{Should I add CDF?}
 The time it took a participant to find a target object is an important indicator of performance for the system, where less time indicates a shorter search time and increased performance.
@@
 
-\todo{update numbers}
 %To compensate for the different numbers of targets found per participant and for each experiment setup, we average each participant's results, giving us 10 samples per experiment. 
@@
 To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
-In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user, enhancing the user experience\todo{maybe cite paper that says less exertion is good}.
+In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user, enhancing the user experience.
+%\todo{maybe cite paper that says less exertion is good}.
 

### 2019-05-06 paper.tex
Fixed table@

@@
   \caption{A summary of the results. }\label{tab:results}
-  \begin{tabular}{ccccc}
+  \begin{tabular}{p{5cm}p{2cm}p{2cm}}
     \toprule
-     & avg & std & avg &std \\ \midrule
+    & \textbf{Guided} & \textbf{Unguided} \\\midrule
+    TAR [\%]           & $46\pm13$ & $54\pm15$   \\\midrule
+    Time to target [s] & $12.5\pm11.9$ & $17.2\pm11.5$ \\\midrule
+    Pan Angle Displacement [rad] & $0.68\pm1.1$ & $0.99\pm1.2$ \\\midrule
+    Tilt Angle Displacement [rad] & $0.68\pm1.1$ & $1.04\pm1.2$ \\\midrule
+    Linear Displacement [rad] & $0.23\pm0.22$ & $0.36\pm0.22$ \\\midrule
     \bottomrule

### 2019-05-06 paper.tex
Edited prev work

@@
 
-Making a mobile device that can detect objects and guide a PwVI in real-time and using on-board processing power has become much more feasible in recent years, thanks to improvements to mobile computing power and image processing methods.
-Early attempts to solve this guidance problem made use of special markers or barcodes, encoded with object or environmental information, and a smartphone that can efficiently scan the environment for these simple patterns~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}.
-The device then uses some feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
-Improvements to feature detectors and deep networks have made it more viable~\cite{redmon2016you,huang2017speed} to replace the markers with real objects, while providing the same guidance functionality.
-The SIFT and SURF-based systems in~\cite{schauerte2012assistive} is an example of a markerless system.
-An alternative detection approach proposed in~\cite{bigham2010vizwiz}, and commercialised in the `Be My Eyes' app~\cite{bemyeyes2019}, requires the user to send a photo of their environment and target object to a Mechanical Turk worker or volunteer that then sends the position of the requested object within the picture back to the user.
+Making a mobile device that can detect objects and guide a PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing power and image processing methods.
+Early attempts to solve this guidance problem made use of special markers encoded with object or environmental information, and a smartphone that can scan the environment for these simple patterns~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}.
+The device uses some feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
+Improvements to feature detectors and deep networks have made it more viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects while providing the same guidance functionality.
+The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
+An alternative detection approach proposed in~\cite{bigham2010vizwiz}, and commercialised in the `Be My Eyes' app~\cite{bemyeyes2019}, requires the user to send the desired object and a photo of their environment to a Mechanical Turk worker or volunteer that sends the position of the requested object within the picture back to the user.
 
-The issue with the marker-based approach is that it requires a significant amount of effort to place and maintain markers around an environment.
-This problem is remedied in the markerless systems.
-However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves first before any guidance can be provided.
-The human-based systems from~\cite{bigham2010vizwiz,bemyeyes2019} can leverage a human's understanding of the environment to help guide a person to the correct area, but the drawback here is that there is a significant lag time and a significant reliance on a good internet connection and remote worker being available.
-Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing a controller that provides the user with instructions on where to point the device to find an out of view object and we proved that this is a viable method to search for an object.
-However, this work relied upon physical barcodes, encoded with object information, to simulate real objects.
-In this work, we are replacing the barcodes with real objects, thereby closing the object detection and guidance loop.
+The issue with the marker-based approach is that it requires a significant amount of effort to place and maintain markers around an environment, which is remedied by markerless systems.
+However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves first before any guidance is provided.
+The systems in~\cite{bigham2010vizwiz,bemyeyes2019} can leverage a human's understanding of the environment to help guide a person to the correct area, but the drawback here is that there is significant lag, and a reliance on a good internet connection and remote worker being available.
+Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that provides the user with pointing instructions to find an out of view object and proved that this is a viable method to search for an object.
+However, this work relied on physical barcodes encoded with object information to simulate real objects.
+In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.
 
-Object detectors can be divided into two main categories that use single-stage and 2-stage methods.  
-The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects.
-They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
-On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
-These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
-Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
-There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
-MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
-This leads to model that uses much less memory, but again with a small drop in accuracy.
+Object detectors can be divided into two main categories: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
+Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
+On the other hand, single-stage models, such as SSD, YOLO and MobileNet~\cite{liu2016ssd,redmon2018yolo,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models.
+%MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
+%The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects.
+%They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
+%On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
+%These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
+%Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
+%There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
+%MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
+%This leads to model that uses much less memory, but again with a small drop in accuracy.
 

### 2019-05-06 paper.tex
Edited activie vision systyem

@@
 
-The work we present in this paper is an advancement towards the ActiVis projects larger goal of developing a stand-alone mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention.
-This work focuses on guiding a user towards an object in one, static environment and is limited to 2 dimensions (pan and tilt).
+The ActiVis project's goal is developing a stand-alone mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
+%This work focuses on guiding a user towards an object in one static environment and is limited to 2 dimensions (pan and tilt).
 
@@
 
-In this case, the error is defined as the difference between the desired object and the object currently within view. 
-The implication of this modification is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
+In this case, the error, $e$, is defined as the difference between the desired object and the object currently within view. 
+The implication of adding a human into the loop is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
 However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
-It is therefore important to design \emph{K} to take be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
+It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
 %These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}
@@
 Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector making classification errors that will influence the action that \emph{K} generates.
-In our previous work, we assumed a `perfect classifier' and solved the problem using a plain Markov decision process (MDP). 
-In this work we do away with that somewhat naive assumption and implement a POMDP that can better handle the observation uncertainties inherent to modern object detectors and classifiers. 
-The design of the human controller is discussed next.
+In our previous work, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
+In this work we do away with that somewhat naive assumption and implement a POMDP that can handle observation uncertainties in object detectors and classifiers.
 

### 2019-05-06 paper.tex
Edited human controller

@@
 \title{ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments}
+\titlerunning{Mobile Object Detection and Active Guidance}
 
@@
 
-The POMDP human control module that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
-It works by generating a trail of virtual waypoints for the user to point the camera towards.
-The waypoint positions are based on the model's pre-trained, internal knowledge on the inter-object spatial relationships and they are placed in a way that maximises the probability of the user pointing to and finding the target object
+The POMDP module that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
+It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads tot he target object.
+The waypoint positions are based on the model's pre-trained internal knowledge on the inter-object spatial relationships and they are placed in a way that maximises the probability of the user pointing to and finding the target object.
 A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.
-The design and implementation of this POMDP human controller is discussed here.
 
@@
 A POMDP is an extension to the MDP model that allows it to handle cases where the state is not directly observable, allowing it to be used in more realistic scenarios. 
-In this case, the state is inferred based on the model parameters and the associated sensor accuracy (if a sensor is 100\% accurate, the state would be directly observable).
-The implication of this is that a POMDP-based agent does not know its state at any point in time.
-Instead, a POMDP model relies on a so-called belief meta-state that changes with additional observations to reflect the likelihood the agent is in any given state.
-The belief state is fully observable by the agent and can be used to infer the parent POMDP-agent's current state and generate the next action, hence the designation as an MDP.\@
+%In this case, the state is inferred based on the model parameters and the associated sensor accuracy (if a sensor is 100\% accurate, the state would be directly observable).
+The implication of this is that a POMDP-based agent does not know its state at any point in time, but must infer it based on the known model parameters and sensor accuracy, the object detector's accuracy in this case.
+This state inference relies on a so-called belief meta-state that is updated with additional observations to reflect the likelihood that the agent is in any given state.
+The belief state is fully observable by the agent and can be used to infer the mobile device's current state and generate the next action.
 
-The system uses an object detector and classifier in order to find any objects within the camera's view.
-These detectors and classifiers have some noise associated with them that is caused by misclassifications and similar errors and a POMDP is therefore necessary in this case.
-
-A POMDP model is represented by the $n$-tuple
+A POMDP model is represented by the $8$-tuple
 
@@
 
-\noindent where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions the agent can execute in any state, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$ after executing action $a$, $a \in \mathbf{A}$ and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a$.
-$\mathbf{\Omega}$ is a set of possible state observations the agent can make, while the table $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
-Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and the scalar $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
-The belief state $\mathbf{b}$ is updated for every timestep and action-observation pair.
-This update is done with
+\noindent where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$, after executing action $a$, $a \in \mathbf{A}$, and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
+$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
+Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
+$\mathbf{b}$ is updated for every timestep and action-observation pair.
+%This update is done with
 
-\begin{equation}
-  b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s), 
-\end{equation}
-where $\eta$ is a normalisation factor.
+%\begin{equation}
+  %b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s), 
+%\end{equation}
+%where $\eta$ is a normalisation factor.
 
-The state and space spaces and the reward and transition functions for this POMDP are the same as the MDP described in~\cite{lock2019active}. 
-The major difference is the addition of an observation matrix that defines the probability of being in any given state after making a new observation.
-In essence, it is a measure of the sensor accuracy, and in this case it describes the object detector's classification accuracy and recall.
-These parameters are given by the following.
+%The state space, reward function and transition matrix are conceptually similar the same as the MDP described in~\cite{lock2019active}. 
+%The major difference is the addition of an observation matrix that defines the probability of being in any given state after making a new observation.
+%In essence, it is a measure of the sensor accuracy, and in this case it describes the object detector's classification accuracy and recall.
+%These parameters are given by the following.
+
+Each of the POMDP's parameters are discussed next.
 
@@
 
-The possible actions an that define the area where the agent will generate the next waypoint are given by
+The possible actions that dictates the location the mobile device will generate the next waypoint are given by
 
 \begin{equation}
-  \mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}
+  \mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}.
 \end{equation}
@@
 
-$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\mathbf{A}$ from the OpenImages~\cite{openimages} dataset. 
-For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e.
-UP) the object `keyboard' in 16\% of images containing both objects.
+$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for a limited number of objects in terms of the actions in $\mathbf{A}$ from the OpenImages~\cite{openimages} dataset. 
+For example, by iterating over the images containing the objects of interest, we can see that the object `monitor' is located above (i.e.
+UP) the object `keyboard' in 16\% of images containing both objects (see Fig.~\ref{fig:openimage}).
 The transition function for this case will look like
@@
 \begin{equation}
-  \mathbf{T}(s, a, s') = \mathbf{T}(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16.
+  t(s, a, s') = t(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16.
 \end{equation}
-An example of this relationship can be seen in the image in Fig.~\ref{fig:openimage}.
+%An image displaying this relationship can be seen in Fig.~\ref{fig:openimage}.
 
@@
 
-The reward function is designed to encourage the agent to find the target object by giving it a substantial reward for doing so, while penalising it for every action it takes that does not results in it finding the target object.
-Furthermore, additional penalties are given if the agent generates a waypoint in an area it has explored before $(v = \textrm{true}$) and when it exceeds some search length threshold, denoted by $n_{\max}$.
-All of the rewards and when they are given are summarised by Table~\ref{tab:rewards}.
+The reward function is designed to encourage the device controller to search for and find the target object by giving it a substantial reward for doing so, while penalising it for every action it takes that does not results in it finding the target object.
+Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) and when it exceeds some search length threshold denoted by $n_{\max}$.
+The rewards are given are summarised in Table~\ref{tab:rewards}.
 
-\begin{table}
+\begin{table}[h]
   \centering
   \caption{The reward function for the POMDP. }\label{tab:rewards}
-  \begin{tabular}{cc}
+  \begin{tabular}{p{3cm}p{1cm}}
     \toprule
@@
 
-The observations the agent can make are identical to the states that the agent can enter. 
-In this case, however, the only uncertainty in the system is introduced by the object detector, since the model can perfectly track the number of steps taken during the search and the locations that waypoints have been generated.
+The observations the controller can make are identical to the states that the mobile device can enter. 
+In this case, however, uncertainty is introduced to the observation by the object detector.
+Previous search locations and search time is perfectly observable in this case, since these can be tracked by the mobile device.
 $\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector. 
@@
 
-For our system, we encoded a total of 16 objects, including a `nothing' state where the detector does not see anything of interest, into the POMDP and object detector.
+We encoded a total of 16 objects, including a `nothing' state where the detector does not see anything of interest, into the controller and object detector.
 These objects are given by $\mathbf{U}$, defined as
@@
     \mathbf{U} = \{ nothing, monitor, keyboard, mouse, desk, laptop, mug, window,\\ 
-      lamp, backpack, chair, couch, plant, telephone, whiteboard, door \}
+      lamp, backpack, chair, couch, plant, telephone, whiteboard, door \}.
   \end{split}
@@
 
-The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that an agent can use to produce the optimal waypoint locations.
-This is done by having the agent explore the entire state-action-observation space and optimising the policy to maximise the long-term cumulative reward.
+The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that the controller can use to produce the optimal waypoint locations.
+This is done by having the model explore the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.
 
-The difficulty of solving POMDPs is that the belief vector is a vector of continuous probability distributions with infinite combinations, making them very time-consuming or even impossible to solve exactly and we found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
-Multiple algorithms that solve POMDPs approximately have been proposed~\cite{bargiacchi2016dynamic,kaelbling1998planning,silver2010monte,spaan2005perseus} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library~\cite{aitoolbox} to solve the POMDP model.
+\todo{maybe remove references here}
+The difficulty of solving POMDPs is that $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
+We found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
+Multiple algorithms have been proposed~\cite{bargiacchi2016dynamic,kaelbling1998planning,silver2010monte,spaan2005perseus} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library~\cite{aitoolbox} to solve the POMDP model.
 The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only.
@@
 
-\subsection{Controller Implementation}
+\subsection{Guidance System Implementation}
 
-We made an Android app that implements the object detector and POMDP controller onto a mobile phone that can generate and provide guidance instructions for a user.  
-This was done by combining an audio interface that can provide non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
+We implemented the object detector and POMDP controller by combining it with an audio interface that provides non-visual guidance instructions onto an Android app.% that can be used by a PwVI by adding .% onto a mobile phone that can generate and provide guidance instructions for a user.
+Non-visual feedback allows the app to be used by PwVI.
+%This was done by combining an audio interface that provides non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
 Each of these aspects and their implementation are discussed here.
@@
 
-The target audience of our system are PwVI and we therefore have to provide guidance instructions in a non-visual manner that is intuitive and easy to understand. 
-To avoid blocking a user's access to the ambient sounds (something PwVI typically rely upon extensively), we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.
+ActiVis's target audience are PwVI and we therefore have to provide guidance instructions in a non-visual manner that is intuitive and easy to understand. 
+To avoid blocking a user's access to ambient sounds (something PwVI typically rely upon), we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.
 
-To describe the waypoints pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
-However, in this work we only spatialise the audio in the pan dimension only, since our headphones bypass the ear's pinnae that allow a person to determine the tilt angle of a sound source. 
-Instead we exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch as a function of the waypoint's tilt angle.
+To describe the waypoints' pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
+However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
+To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch as a function of the waypoint's tilt angle.
 A similar interface was used in~\cite{schauerte2012assistive}.
@@
 
-The SSD-Lite network is a single-stage object detection network that is based on the SSD architecture, but uses MobileNetV2~\cite{sandler2018mobilenetv2} for its backbone.
-This leads to a more `lightweight' model that has less parameters and requires less memory to perform inference tasks, which makes it suitable for a mobile platform. 
+The SSD-Lite network is a single-stage object detection and classification network that is based on the SSD architecture that uses MobileNetV2~\cite{sandler2018mobilenetv2} for its backbone.
+This is a lightweight model that has less parameters and requires relatively little memory to perform inference tasks, which makes it suitable for mobile platforms. 
 This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
-When compared with the full SSD model, it achieves a slightly lower mAPs (0.25), but with significantly less parameters (34.3M) and FLOPS (34.36B).
-Tiny-DSOD~\cite{li2018tinydsod} is another object detection network focussed on mobile compatibility that is an alternative to the SSD-Lite network with similar accuracy and computing requirements(mAPs$=0.23$, parameters$=$1.15M, FLOPS$=$1.12B).
+The full SSD model on the other hand achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
+Tiny-DSOD~\cite{li2018tinydsod} is a mobile alternative to SSD-Lite with similar accuracy and computing requirements(mAPs$=0.23$, parameters$=$1.15M, FLOPS$=$1.12B).
 However, we found that the SSD-Lite version produced better results in this application and we chose to implement it into our system.
 
-The network was trained with a maximum of 10000 annotated object samples for each object class in $\mathbf{A}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
-The images were taken from the OpenImages~\cite{openimages} dataset.
+The network was trained with a maximum of 10000 annotated object samples, taken from the OpenImages dataset~\cite{openimages}, for each object class in $\mathbf{A}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
 We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
@@
 
-\subsubsection{POMDP Controller}
+\subsubsection{Controller}
 
 The output from the POMDP model's training process is a policy file that defines the best location to place the next search waypoint based on the device's current state.
-This state is tracked by the device during run-time by recording the device's previous search locations and previous waypoint positions, which is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
-Each grid square represents a \SI{35}{\degree} angular translation, encompassing a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
-This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation parameter $o$ is generated by the object detector.
+This state is tracked by the device throughout the app's runtime by performing object detection and recording the device's previous search locations and previous waypoint positions
+The latter is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
+Each grid square represents a \SI{35}{\degree} angular translation and the grid encompasses a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
+This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector.
 
-When the user moves the device into a new grid square by rotating the device past \SI{35}{\degree}, thereby making a new $v$ observation and changing the state, or observes a new object, the device triggers the controller to generate a new waypoint location.
-The controller uses the new state observation $\omega$ to update its belief state and queries the policy for the best location to place the new waypoint. 
-The policy output is an action from the action set $\mathbf{A}$ that specifies the next adjacent grid square to place the waypoint.
-For example, an `UP' output would result in the waypoint being placed one grid square, i.e. \SI{35}{\degree}, above where the current grid square within view.
+When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} and moves the device into a new grid square or sees a new object, the device triggers the controller to generate a new waypoint location.
+The controller uses the new $\omega$ to update $\mathbf{b}$ queries the policy for the best location to place the new waypoint. 
+The policy output is an action from the action set $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint.
+For example, an `UP' output would result in the waypoint being placed one grid square above the current grid square within view.
 

### 2019-05-06 paper.tex
Edited experiment section

@@
 \institute{University of Lincoln, Lincoln, UK \and
-  Universita Degli Studi Di Padova, Italy
+  Universit\`{a} degli studi di Padova, Italy
 }
@@
 
-To evaluate the effectiveness of our POMDP controller and guidance system, we designed a set of experiments that can measure its performance in driving a user towards a target object within the environment.
-We also conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement to compare our results to and provide additional context. 
-This alternative `guidance' system does not actually provide any guidance instructions to the user, instead it provides the user with the raw observation output from the object classifier and makes use of the user's intuition and prior environment knowledge to generate actions.
-The goal of both the guided and unguided experiment cases were to find an object within a static environment.
+To evaluate the guidance system's effectiveness, we designed a set of experiments to measure its performance in driving a user towards a target object within a static environment. 
+We also conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement for our system's results. 
+This alternative system does not provide any guidance instructions to the user.
+Instead, it provides the user with the raw observations from the object classifier and makes use of the user's own intuition and prior environment knowledge to generate actions. 
+%The goal of both the guided and unguided experiment cases were to find an object within a static environment.
 
-We recruited 10 participants (8 male, 2 female; average age 24.2 years) for the experiments, including 2 legally blind participants, where 1 was blind from birth and the other suffers from late onset blindness.
-Details on the design of these experiments are given in the next sections.
+We recruited 10 participants (8 male, 2 female; average age 24.2 years) for the experiments, including 2 legally blind participants, where 1 was blind from birth and the other has late onset blindness.
+The other 8 participants were blindfolded for the experiments. 
+The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore~\footnote{developers.google.com/ar/} and text-to-speech enabled.
 
@@
 
-The design goal of this experiment is to mimic how a typical person with healthy eyesight would behave if told to look for a given object. 
-In such a scenario, a person would exploit the objects currently within their view and their prior knowledge on a room's typical layout to make a decision on where to look next to find what they are looking for.
-Take for example a person in bathroom facing the basin after washing their hands and looking for a hand-dryer. 
-It is unlikely that a hand dryer would be placed above or below a wash basin so it it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them to find a dryer.
+The goal of this experiment is to mimic how a typical person with normal eyesight would behave if told to look for an object. 
+In such a scenario, a person would see the objects currently within their view and use their prior knowledge on a room's typical layout to make a decision on where to look next.
+Take for example a person in bathroom facing the basin after washing their hands and looking for a hand-dryer: it is unlikely that a hand dryer would be placed above or below a wash basin so it it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them to find a dryer.
 
-For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object.
-This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller}, \emph{H}, acts as both the actuator and controller.
-The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
-The app only reads out the objects when the participant requested it to by tapping on the screen. 
-When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.
+For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view.
+It is then up to the participant to exploit their prior knowledge of the given environment and manipulate the camera to point it towards the target object. 
+This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller} where the human acts as both the actuator and controller.
+The app only reads out the objects upon the user's request by tapping on the screen. 
+When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.
 
@@
 
-Each participant was verbally told what the target object was they they were meant to find and each participant was given 45 seconds to find the target object. 
-In this case, the learning effect was ignored in order to mimic the typical search behaviour described earlier. 
+Each participant was verbally informed prior to each experiment run what the target object was and they were given 45 seconds to find it.
 Each experiment run was ended when a target was found or the time limit was reached. 
+In this case, the learning effect was ignored in order to mimic the typical search behaviour and allow proper use of prior knowledge. 
 This process was repeated a total of 8 times, once for each target object within the environment.
@@
 
-In this experiment, we evaluate the performance of the guidance system in the object search task, where the perception and control tasks are performed by the guidance system and mobile device and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor.
-This is modelled by the schematic in Fig.~\ref{fig:sys-diagram}.
+In this experiment, we evaluate the performance of the guidance system in the object search task, where the perception and control tasks are performed by the guidance system and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor.
+This is modelled in the schematic in Fig.~\ref{fig:sys-diagram}.
 
 The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object themselves.
-An experiment run was therefore initiated when the experiment staff selected the target and was terminated when the target object was found or the time limit was exceeded.
+This also isolated the performance measurement to the system alone.
+An experiment run was therefore when the experiment staff selected the target and was terminated when the target object was found or the 45 second time limit was reached.
 We set a time limit of 45 seconds in this experiment as well.
@@
 
-The environment, and the object placement within it, for both experiments was modelled on a typical office.
+The environment and the object placement within it for both experiments was modelled on a typical office.
 Measures were taken to ensure that both office environments were unique in layout and object placement. 

### 2019-05-06 paper.tex
Edit to spacing and removed equations

@@
 \begin{itemize}
-  \item a POMDP-based human controller that enables object search and guidance on a mobile phone;
-  \item a complete system pipeline that includes guidance instruction generation and transmission;
+  \item a controller that enables object search and guidance on a mobile phone;
+  \item a complete system pipeline that includes interfacing, object detection and human control;
   \item experiments that evaluate the efficacy of the proposed system.
@@
 
-The ActiVis project's goal is developing a stand-alone mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
+The ActiVis project's goal is developing a mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
 %This work focuses on guiding a user towards an object in one static environment and is limited to 2 dimensions (pan and tilt).
@@
 
-\begin{equation}
+\begin{equation*}
   (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma),
-\end{equation}
+\end{equation*}
 
@@
 $\mathbf{b}$ is updated for every timestep and action-observation pair.
+Each of the POMDP's parameters are discussed next. 
 %This update is done with
@@
 
-Each of the POMDP's parameters are discussed next.
-
 \subsubsection{State Space}
 
-The state is given by
-
-\begin{equation}
-  s = \langle u, n, v \rangle,
-\end{equation}
-
-\noindent where $u, u\in\mathbf{U}$, is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
+The state is given by $s = \langle u, n, v \rangle$, where $u, u\in\mathbf{U}$, is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
 
@@
 
-The possible actions that dictates the location the mobile device will generate the next waypoint are given by
-
-\begin{equation}
-  \mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}.
-\end{equation}
+The possible actions that dictates the location the mobile device will generate the next waypoint are given by $\mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}$.
 
@@
 UP) the object `keyboard' in 16\% of images containing both objects (see Fig.~\ref{fig:openimage}).
-The transition function for this case will look like
+The transition function for this case is $t(s, a, s') = t(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16$.
 
-\begin{equation}
-  t(s, a, s') = t(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16.
-\end{equation}
+%\begin{equation*}
+  %t(s, a, s') = t(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16.
+%\end{equation*}
 %An image displaying this relationship can be seen in Fig.~\ref{fig:openimage}.
@@
 Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) and when it exceeds some search length threshold denoted by $n_{\max}$.
-The rewards are given are summarised in Table~\ref{tab:rewards}.
+The rewards are summarised in Table~\ref{tab:rewards}.
 
@@
 
-\begin{equation}
+\begin{equation*}
   \begin{split}
@@
   \end{split}
-\end{equation}
+\end{equation*}
 
@@
 
-\begin{equation}
+\begin{equation*}
   u_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
-\end{equation}
+\end{equation*}
 while the objects in the unguided experiment are
 
-\begin{equation}
+\begin{equation*}
   u_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
-\end{equation}
+\end{equation*}
 %A picture of the unguided experiment environment is given in Fig.~\ref{fig:experiment-env}.
@@
 
+%For example, a TAR of 0.5 indicates that a participant found the target objects 50\% of searches. 
+%We set an upper time limit for each object search run of 45 seconds.
+%When this upper threshold was reached, the search was recorded as a failure and the next run was started.
+
 The target acquisition rate (TAR) is the proportion of experiment runs where the participant successfully found the target object with each respective system. 
-For example, a TAR of 0.5 indicates that a participant found the target objects 50\% of searches. 
-We set an upper time limit for each object search run of 45 seconds.
-When this upper threshold was reached, the search was recorded as a failure and the next run was started.
-
-We found that the unguided case produced a higher average TAR than the guided case (0.54 vs.
-0.46), meaning that a participant was more around 8\% more likely to find more objects without our guidance than with it.
-However, the Kruskal-Wallis test for non-normal data shows that these sets of results are not statistically significantly different from one another ($p = 0.16$), meaning we are unable to conclude which approach produced better results.
-The results are summarised in Table~\ref{tab:results}.
+By taking each participant's TAR as a datum, we found that the unguided case produced a higher average TAR than the guided case (0.54 vs.
+0.46), meaning that a participant found 8\% more objects without guidance.
+However, the Kruskal-Wallis (KW) test for non-normal data shows that these results are not statistically significantly different from one another ($p_{kw} = 0.16$), meaning we are unable to conclude which experiment produced better results.
+All of the experiment results are summarised in Table~\ref{tab:results}.
 
@@
   \centering
-  \caption{A summary of the results. }\label{tab:results}
-  \begin{tabular}{p{5cm}p{2cm}p{2cm}}
+  \caption{A summary of the experiment results. }\label{tab:results}
+  \begin{tabular}{p{5cm}p{2cm}p{2cm}p{2.5cm}}
     \toprule
-    & \textbf{Guided} & \textbf{Unguided} \\\midrule
-    TAR [\%]           & $46\pm13$ & $54\pm15$   \\\midrule
-    Time to target [s] & $12.5\pm11.9$ & $17.2\pm11.5$ \\\midrule
-    Pan Angle Displacement [rad] & $0.68\pm1.1$ & $0.99\pm1.2$ \\\midrule
-    Tilt Angle Displacement [rad] & $0.68\pm1.1$ & $1.04\pm1.2$ \\\midrule
-    Linear Displacement [rad] & $0.23\pm0.22$ & $0.36\pm0.22$ \\\midrule
+    & \textbf{Guided} & \textbf{Unguided}  & \textbf{KW Statistic} \\\midrule
+    TAR [\%]           & $46\pm13$ & $54\pm15$ &  0.16 \\\midrule
+    Time to target [s] & $12.5\pm11.9$ & $17.2\pm11.5$ & 0.045 \\\midrule
+    Pan Angle Displacement [rad] & $0.68\pm1.1$ & $0.99\pm1.2$ & 0.029 \\\midrule
+    Tilt Angle Displacement [rad] & $0.68\pm1.1$ & $1.04\pm1.2$ & 0.011 \\\midrule
+    Linear Displacement [rad] & $0.23\pm0.22$ & $0.36\pm0.22$ & 0.012 \\\midrule
     \bottomrule
@@
 The time it took a participant to find a target object is an important indicator of performance for the system, where less time indicates a shorter search time and increased performance.
-The data for the search times for each dataset are given in Fig~\ref{fig:boxplot-time}.%, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
+The data for the search times for each dataset are displayed in Fig~\ref{fig:boxplot-time}.%, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
 
-\begin{figure}
+\begin{figure}[h]
   \centering
   \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
-  \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
+  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
 \end{figure}
@@
 %To compensate for the different numbers of targets found per participant and for each experiment setup, we average each participant's results, giving us 10 samples per experiment. 
-By inspecting the boxplots in Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
-This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p=0.045$).
-These results are summarised in Table~\ref{tab:results}. 
-With this 27\% reduction in total time spent searching for a target object, we can conclude that a user benefits from using our smart guidance system, as opposed to relying on a simple object reader. 
+From Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
+This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$).
+%These results are summarised in Table~\ref{tab:results}. 
+%With this 27\% reduction in total time spent searching for a target object, we can conclude that a user benefits from using our smart guidance system as opposed to relying on a simple object reader. 
 %This is supported by the CDFs in Fig.~\ref{fig:cum-time} that show that \todo{Discuss the less number of objects found and how it is not statistically signioficatn. Perhaps show it in CDF}
@@
 To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
-In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user, enhancing the user experience.
+In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user, enhancing the user experience and improving ease of use.
 %\todo{maybe cite paper that says less exertion is good}.
 
-The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ (tilt) dimensions.
-By integrating these data we can obtain and compare the total absolute displacement for each dimension.
-The angle and distance results are plotted in the boxplots in Figs.~\ref{fig:boxplot-angle} and~\ref{fig:boxplot-dist} respectively.
+The device displacement was measured in both linear ($x, y, z$) and angular (pan, tilt) dimensions.
+By integrating these data we obtain and compare the total absolute displacement in each dimension.
+These results are plotted in Fig.~\ref{fig:boxplot-displacement}.
+
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.7\textwidth]{figures/boxplot_angle.png}
+  %\caption{A set of boxplots comparing the angular distance the device travelled for each experiment. }\label{fig:boxplot-angle}
+%\end{figure}
+
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.7\textwidth]{figures/boxplot_dist.png}
+  %\caption{A set of boxplots comparing the distance the device travelled for each experiment. }\label{fig:boxplot-dist}
+%\end{figure}
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/boxplot_angle.png}
-  \caption{A set of boxplots comparing the angular distance the device travelled for each experiment. }\label{fig:boxplot-angle}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{figures/boxplot_dist.png}
-  \caption{A set of boxplots comparing the distance the device travelled for each experiment. }\label{fig:boxplot-dist}
+  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
+  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
 \end{figure}
@@
 The boxplots for the total angle displacement show a consistent reduction in radians for the guided case for both the pan (\SI{0.68}{\radian} vs.
-\SI{0.99}{\radian}, $p=0.029$) and tilt dimensions (\SI{0.68}{\radian} vs.
-\SI{1.05}{\radian}, $p=0.011$).
+\SI{0.99}{\radian}, $p_{kw}=0.029$) and tilt dimensions (\SI{0.68}{\radian} vs.
+\SI{1.05}{\radian}, $p_{kw}=0.011$).
 The guidance system therefore reduces the total angular displacement to find the objects by 31\% and 35\% for the pan and tilt dimensions respectively. 
-The total linear displacement is also reduced when using the guidance interface by approximately 36\% (\SI{0.23}{\metre} vs. \SI{0.36}{\metre}, $p=0.012$).
+The total linear displacement is also reduced when using the guidance interface by approximately 36\% (\SI{0.23}{\metre} vs. \SI{0.36}{\metre}, $p_{kw}=0.012$).
 These results are summarised in Table~\ref{tab:results}.
@@
 We implemented this system into an Android app and tested it with a group of 10 participants to evaluate its effectiveness compared to a baseline, unguided case that only uses the object detector and relies on the human to generate their own search path.
-The key results from these experiment is that the guidance system improved the participants' target-finding performance, reducing the search time and overall camera manipulation effort required.
+The key results from these experiment is that the guidance system improved the participants' target-finding performance, reducing the search time and overall camera manipulation effort required when compared to a base case.
 However, the participants were able to find 8\% more objects on average in the unguided case, but this result was found to be statistically insignificant. 
+With these results, we can reasonably conclude that our system enables a blind or blindfolded user to find a target object and does so better than the alternative base case.
 

### 2019-05-06 paper.tex
MOre edits

@@
 
-\author{Jacobus C. Lock\inst{1} \and
-  Grzegorz Cielniak\inst{1} \and
-  Andrea G. Tramontano\inst{2} \and
-  Nicola Bellotto\inst{1}
+\author{J.C. Lock\inst{1} \and
+  G. Cielniak\inst{1} \and
+  A.G. Tramontano\inst{2} \and
+  N. Bellotto\inst{1}
 }
@@
 
-It is estimated that there are almost half a billion people today that live with mild to severe levels of vision impairments or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
+There are an estimated half a billion people that live with mild to severe vision impairment or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
 There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
 The work we present here is part of the ActiVis project that aims to assist people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
-This system implements ideas from the active vision field~\cite{bajcsy2017,bellotto2013}, but replaces the electro-mechanical servo typically found in active vision systems, with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
-This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.
+This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
+This project expands upon concepts proposed in~\cite{bellotto2013,lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.
 
@@
 
-Our active search system uses the camera's current and previous views as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to determine the best action to take to reach the target object.
-To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.
+ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to take to reach the target object.
+To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone that generates real-time navigation instructions to guide the user to their target object.
 This work makes the following contributions:
@@
 
-Section~\ref{sec:previous-work} discusses relevant work that has already been done, followed by a description of the active vision system and human controller in Sections~\ref{sec:active-vision} and~\ref{sec:human-controller} respectively.
-The experiments that were conducted in this work, and their results, are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.
+Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and human controller in Sections~\ref{sec:active-vision} and~\ref{sec:human-controller} respectively.
+The experiments that were conducted in this work and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.
 
@@
 
-Making a mobile device that can detect objects and guide a PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing power and image processing methods.
-Early attempts to solve this guidance problem made use of special markers encoded with object or environmental information, and a smartphone that can scan the environment for these simple patterns~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}.
-The device uses some feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
-Improvements to feature detectors and deep networks have made it more viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects while providing the same guidance functionality.
-The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
-An alternative detection approach proposed in~\cite{bigham2010vizwiz}, and commercialised in the `Be My Eyes' app~\cite{bemyeyes2019}, requires the user to send the desired object and a photo of their environment to a Mechanical Turk worker or volunteer that sends the position of the requested object within the picture back to the user.
+%Mobile devices that can detect objects and guide PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing and image processing methods.
+Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}.
+The device uses a feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
+Improvements to feature detectors have made it viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects while providing the same guidance functionality.
+%The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
+An alternative detection approach proposed in~\cite{bigham2010vizwiz} requires the user to send a photo of their environment to a Mechanical Turk worker that sends the position of the requested object within the picture back to the user.
 
-The issue with the marker-based approach is that it requires a significant amount of effort to place and maintain markers around an environment, which is remedied by markerless systems.
-However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves first before any guidance is provided.
-The systems in~\cite{bigham2010vizwiz,bemyeyes2019} can leverage a human's understanding of the environment to help guide a person to the correct area, but the drawback here is that there is significant lag, and a reliance on a good internet connection and remote worker being available.
-Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that provides the user with pointing instructions to find an out of view object and proved that this is a viable method to search for an object.
-However, this work relied on physical barcodes encoded with object information to simulate real objects.
+The issue with a marker-based approach is that it requires significant effort to place and maintain them in an environment, which is remedied by markerless systems.
+However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
+The system in~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to help guide a user to the correct location, but the there is significant lag and a reliance on a good internet connection and remote worker being available.
+Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that provides the user with pointing instructions to find an out-of-view object and proved that this is a viable method to search for an object.
+However, this work used barcodes encoded with object information to simulate real objects.
 In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.
 
-Object detectors can be divided into two main categories: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
+Object detectors mainly come in 2 flavours: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
 Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
@@
 
-Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector making classification errors that will influence the action that \emph{K} generates.
+Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector's classification errors that influence the action that \emph{K} generates.
 In our previous work, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
-In this work we do away with that somewhat naive assumption and implement a POMDP that can handle observation uncertainties in object detectors and classifiers.
+In this work we do away with that somewhat naive assumption and implement a POMDP that can handle classification uncertainties in object detectors and classifiers.
 
@@
 
-The POMDP module that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
-It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads tot he target object.
-The waypoint positions are based on the model's pre-trained internal knowledge on the inter-object spatial relationships and they are placed in a way that maximises the probability of the user pointing to and finding the target object.
-A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.
+The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
+It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
+The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
+%A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.
 
@@
 
-A POMDP model is represented by the $8$-tuple
-
-\begin{equation*}
-  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma),
-\end{equation*}
-
-\noindent where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$, after executing action $a$, $a \in \mathbf{A}$, and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
+A POMDP model is represented by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$, after executing action $a$, $a \in \mathbf{A}$, and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
 $\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
 Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
-$\mathbf{b}$ is updated for every timestep and action-observation pair.
+%$\mathbf{b}$ is updated for every timestep and action-observation pair.
 Each of the POMDP's parameters are discussed next. 
@@
 
-The reward function is designed to encourage the device controller to search for and find the target object by giving it a substantial reward for doing so, while penalising it for every action it takes that does not results in it finding the target object.
-Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) and when it exceeds some search length threshold denoted by $n_{\max}$.
+The reward function encourages the device controller to search for and find the target object by giving it a substantial reward for doing so, while penalising it for every action that does not result in it finding the target object.
+Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) or when it exceeds some search length threshold denoted by $n_{\max}$.
 The rewards are summarised in Table~\ref{tab:rewards}.
 
-\begin{table}[h]
+\begin{table}
   \centering
@@
 
-The observations the controller can make are identical to the states that the mobile device can enter. 
-In this case, however, uncertainty is introduced to the observation by the object detector.
-Previous search locations and search time is perfectly observable in this case, since these can be tracked by the mobile device.
+The state observations are identical to the states that the mobile device can enter. 
+In this case, however, uncertainty is introduced into the observation by the object detector.
+Previous search locations and search time are fully observable here, since they can be tracked by the mobile device.
 $\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector. 
@@
 
-We encoded a total of 16 objects, including a `nothing' state where the detector does not see anything of interest, into the controller and object detector.
-These objects are given by $\mathbf{U}$, defined as
+We encoded 16 objects, including a `nothing' object where the detector does not see anything of interest, into the controller and object detector.
+These objects are defined as
 
@@
 
-We also set $n_{\max}$ to 12 waypoints, after which the agent gets penalised for every additional waypoint it generates that does not lead to the target object. 
+\noindent We set $n_{\max}$ to 12 waypoints, after which the agent gets penalised for every additional waypoint it generates that does not lead to the target object. 
 This results in a total of 352 reachable states ($n_{states} = 16\times11\times2$), with any state containing the target object acting as a terminal state.
@@
 This is done by having the model explore the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.
-
-\todo{maybe remove references here}
 The difficulty of solving POMDPs is that $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
 We found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
-Multiple algorithms have been proposed~\cite{bargiacchi2016dynamic,kaelbling1998planning,silver2010monte,spaan2005perseus} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library~\cite{aitoolbox} to solve the POMDP model.
-The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only.
+Multiple algorithms have been proposed~\cite{bargiacchi2016dynamic,silver2010monte} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library~\footnote{github.com/Svalorzen/AI-Toolbox} to solve the POMDP model.
+The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking these points only. 
 Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.
@@
 
-ActiVis's target audience are PwVI and we therefore have to provide guidance instructions in a non-visual manner that is intuitive and easy to understand. 
-To avoid blocking a user's access to ambient sounds (something PwVI typically rely upon), we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.
+ActiVis's target audience are PwVI and therefore provides guidance instructions in a non-visual manner that is intuitive and easy to understand. 
+To avoid blocking a user's access to ambient sounds, we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.
 
@@
 However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
-To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch as a function of the waypoint's tilt angle.
-A similar interface was used in~\cite{schauerte2012assistive}.
-With this interface and set of headphones, we are able to describe the location of a waypoint to a user in 2 dimensions (pan and tilt) in an intuitive an non-intrusive manner.
+To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly.
+A similar approach was used in~\cite{schauerte2012assistive}.
+With this interface and headset, ActiVis is able to describe location of a waypoint to a user in the pan and tilt dimensions.
 
@@
 
-The SSD-Lite network is a single-stage object detection and classification network that is based on the SSD architecture that uses MobileNetV2~\cite{sandler2018mobilenetv2} for its backbone.
-This is a lightweight model that has less parameters and requires relatively little memory to perform inference tasks, which makes it suitable for mobile platforms. 
+SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
+This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
 This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
-The full SSD model on the other hand achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
-Tiny-DSOD~\cite{li2018tinydsod} is a mobile alternative to SSD-Lite with similar accuracy and computing requirements(mAPs$=0.23$, parameters$=$1.15M, FLOPS$=$1.12B).
-However, we found that the SSD-Lite version produced better results in this application and we chose to implement it into our system.
+The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
+Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.
 
-The network was trained with a maximum of 10000 annotated object samples, taken from the OpenImages dataset~\cite{openimages}, for each object class in $\mathbf{A}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
+The network was trained with a maximum of 10000 object samples, taken from the OpenImages dataset~\cite{openimages}, for each object class in $\mathbf{U}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
 We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
@@
 
-When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} and moves the device into a new grid square or sees a new object, the device triggers the controller to generate a new waypoint location.
-The controller uses the new $\omega$ to update $\mathbf{b}$ queries the policy for the best location to place the new waypoint. 
-The policy output is an action from the action set $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint.
-For example, an `UP' output would result in the waypoint being placed one grid square above the current grid square within view.
+When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
+The controller uses $\omega$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
+The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.\ `UP' output would result in a waypoint being placed one grid square above the grid square within view.
 

### 2019-05-06 paper.tex
EdItInG

@@
 
-\subsubsection{Controller}
+\subsubsection{Action Generator}
 
@@
 To evaluate the guidance system's effectiveness, we designed a set of experiments to measure its performance in driving a user towards a target object within a static environment. 
-We also conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement for our system's results. 
+We conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement for our system's results. 
 This alternative system does not provide any guidance instructions to the user.
-Instead, it provides the user with the raw observations from the object classifier and makes use of the user's own intuition and prior environment knowledge to generate actions. 
+Instead, it provides the user with raw observations from the object classifier and relies on the user's intuition and prior knowledge to generate actions. 
 %The goal of both the guided and unguided experiment cases were to find an object within a static environment.
 
-We recruited 10 participants (8 male, 2 female; average age 24.2 years) for the experiments, including 2 legally blind participants, where 1 was blind from birth and the other has late onset blindness.
-The other 8 participants were blindfolded for the experiments. 
+We recruited 10 participants (8 male, 2 female; average age 29.2 years) for the experiments, including 2 legally blind participants. 
+The other 8 participants were blindfolded to simulate blindness. 
 The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore~\footnote{developers.google.com/ar/} and text-to-speech enabled.
@@
 
-The goal of this experiment is to mimic how a typical person with normal eyesight would behave if told to look for an object. 
-In such a scenario, a person would see the objects currently within their view and use their prior knowledge on a room's typical layout to make a decision on where to look next.
-Take for example a person in bathroom facing the basin after washing their hands and looking for a hand-dryer: it is unlikely that a hand dryer would be placed above or below a wash basin so it it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them to find a dryer.
+The goal of this experiment is to mimic a typical person with healthy eyesight's search behaviour. 
+In such a scenario, a person would see the objects currently within their field of view and use their prior knowledge and intuition to make a decision on where to look next.
+For example, a person in bathroom facing the basin after washing their hands is unlikely to find a hand dryer placed above or below the basin so it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them instead.
 
-For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view.
-It is then up to the participant to exploit their prior knowledge of the given environment and manipulate the camera to point it towards the target object. 
+For this experiment, the mobile camera and object detector acts as the participants' eyes and informs them about the objects within the camera's view.
+It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
 This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller} where the human acts as both the actuator and controller.
@@
 
-Each participant was verbally informed prior to each experiment run what the target object was and they were given 45 seconds to find it.
-Each experiment run was ended when a target was found or the time limit was reached. 
-In this case, the learning effect was ignored in order to mimic the typical search behaviour and allow proper use of prior knowledge. 
-This process was repeated a total of 8 times, once for each target object within the environment.
+Each participant was verbally informed prior to each experiment what the target object was and they were given 45 seconds to find it and each run was ended when a target was found or the time limit was reached.
+The learning effect was ignored in order to mimic the normal search behaviour described earlier and allow full use of prior knowledge. 
+This process performed once for each object in the experiment set.
 
@@
 
-In this experiment, we evaluate the performance of the guidance system in the object search task, where the perception and control tasks are performed by the guidance system and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor.
+In this experiment, we evaluate the performance of the guidance system in an object search task, where the perception and control tasks are performed by the guidance system and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor.
 This is modelled in the schematic in Fig.~\ref{fig:sys-diagram}.
 
-The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object themselves.
-This also isolated the performance measurement to the system alone.
-An experiment run was therefore when the experiment staff selected the target and was terminated when the target object was found or the 45 second time limit was reached.
-We set a time limit of 45 seconds in this experiment as well.
-Each participant repeated this experiment 8 times, once for each object within the experiment's object set.
+The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object faster themselves.
+This also isolated the performance measurement to the guidance system alone.
+An experiment run started with the experiment staff selecting the target and was terminated when the target object was found or the 45 second time limit was reached.
+This process performed once for each object in the experiment set.
 
@@
 These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
-The objects in the guided experiment environment is
+The objects in the guided experiment environment are
 
 \begin{equation*}
-  u_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
+  \mathbf{u}_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
 \end{equation*}
@@
 \begin{equation*}
-  u_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
+  \mathbf{u}_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
 \end{equation*}
@@
 
-%For example, a TAR of 0.5 indicates that a participant found the target objects 50\% of searches. 
 %We set an upper time limit for each object search run of 45 seconds.
@@
 
-The target acquisition rate (TAR) is the proportion of experiment runs where the participant successfully found the target object with each respective system. 
-By taking each participant's TAR as a datum, we found that the unguided case produced a higher average TAR than the guided case (0.54 vs.
-0.46), meaning that a participant found 8\% more objects without guidance.
-However, the Kruskal-Wallis (KW) test for non-normal data shows that these results are not statistically significantly different from one another ($p_{kw} = 0.16$), meaning we are unable to conclude which experiment produced better results.
-All of the experiment results are summarised in Table~\ref{tab:results}.
+The target acquisition rate (TAR) is the proportion of objects the participants successfully found during an experiment. 
+For example, a TAR of 0.5 indicates that a participant found the target object in 50\% of searches. 
+Taking each participant's TAR as a datum, we found the unguided case produced a higher average TAR (0.54 vs.
+0.46), meaning that a participant found around 8\% more objects without guidance instructions.
+However, the Kruskal-Wallis (KW) test for non-normal data shows that these results are statistically not significantly different from one another ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR.
+All the experiment results are summarised in Table~\ref{tab:results}.
 
@@
 %\todo{Should I add CDF?}
-The time it took a participant to find a target object is an important indicator of performance for the system, where less time indicates a shorter search time and increased performance.
-The data for the search times for each dataset are displayed in Fig~\ref{fig:boxplot-time}.%, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
+The time it takes to find a target object is an important indicator of system performance, where less time indicates a shorter search time and increased performance.
+The data for the search times for each experiment are shown in Fig.~\ref{fig:boxplot-time}.%, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
 
@@
 From Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
-This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$).
+This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
 %These results are summarised in Table~\ref{tab:results}. 
@@
 To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
-In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user, enhancing the user experience and improving ease of use.
+In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user.%, enhancing user experience and improving ease of use.
 %\todo{maybe cite paper that says less exertion is good}.
@@
 
-\begin{figure}
+\begin{figure}[h]
   \centering
@@
 
-In this work, we present a mobile guidance system that uses an object detector to scan the environment for objects and a POMDP-based controller and audio interface to present the user with guidance instructions.
-We implemented this system into an Android app and tested it with a group of 10 participants to evaluate its effectiveness compared to a baseline, unguided case that only uses the object detector and relies on the human to generate their own search path.
-The key results from these experiment is that the guidance system improved the participants' target-finding performance, reducing the search time and overall camera manipulation effort required when compared to a base case.
+In this work, we presented ActiVis, a mobile guidance system that uses an object detector to scan the environment for objects and a POMDP-based controller and audio interface to generate and present the user with guidance instructions.
+We implemented this system on an Android app and tested it with a group of 10 participants to evaluate its effectiveness compared to a baseline, unguided case that only uses the object detector and relies on the human to generate the search path.
+The key results from these experiment is that the guidance system improved the participants' target-searching performance, reducing the total search time and overall camera manipulation effort required when compared to a base case.
 However, the participants were able to find 8\% more objects on average in the unguided case, but this result was found to be statistically insignificant. 

### 2019-05-06 paper.tex
Changes to bib

@@
 Measures were taken to ensure that both office environments were unique in layout and object placement. 
-However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, since most offices contain the same basic furniture and objects. 
+However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, which is not a problem since most offices contain the same basic furniture and objects. 
 These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 

### 2019-05-06 paper.tex
Removed env setting section

--- 2019-05-06 paper.tex
@@
 We found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
-Multiple algorithms have been proposed~\cite{bargiacchi2016dynamic,silver2010monte} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library~\footnote{github.com/Svalorzen/AI-Toolbox} to solve the POMDP model.
+Multiple algorithms have been proposed~\cite{bargiacchi2016dynamic,silver2010monte} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library\footnote{github.com/Svalorzen/AI-Toolbox} to solve the POMDP model.
 The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking these points only. 
@@
 To evaluate the guidance system's effectiveness, we designed a set of experiments to measure its performance in driving a user towards a target object within a static environment. 
-We conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement for our system's results. 
-This alternative system does not provide any guidance instructions to the user.
-Instead, it provides the user with raw observations from the object classifier and relies on the user's intuition and prior knowledge to generate actions. 
+We conducted an additional set of experiments with an alternative system that relies on a user's intuition and prior knowledge to generate actions instead, to act as a baseline measurement for our system's results.
+%This alternative system does not provide any guidance instructions to the user.
+%Instead, it provides the user with raw observations from the object classifier and relies on the user's intuition and prior knowledge to generate actions. 
 %The goal of both the guided and unguided experiment cases were to find an object within a static environment.
+
+Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement. 
+However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences which is not a problem since most offices contain the same basic furniture and objects. 
+The objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects between experiments. 
+The objects in the guided experiment environment are
+
+\begin{equation*}
+  \mathbf{u}_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
+\end{equation*}
+while the objects in the unguided experiment are
+
+\begin{equation*}
+  \mathbf{u}_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
+\end{equation*}
 
@@
 The other 8 participants were blindfolded to simulate blindness. 
-The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore~\footnote{developers.google.com/ar/} and text-to-speech enabled.
+The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{developers.google.com/ar/} and text-to-speech enabled.
 
@@
 
-\subsection{Environment Setup}
+%\subsection{Environment Setup}
 
-The environment and the object placement within it for both experiments was modelled on a typical office.
-Measures were taken to ensure that both office environments were unique in layout and object placement. 
-However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, since most offices contain the same basic furniture and objects. 
-These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
-The objects in the guided experiment environment are
+%The environment and the object placement within it for both experiments was modelled on a typical office.
+%Measures were taken to ensure that both office environments were unique in layout and object placement. 
+%However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, which is not a problem since most offices contain the same basic furniture and objects. 
+%These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
+%The objects in the guided experiment environment are
 
-\begin{equation*}
-  \mathbf{u}_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
-\end{equation*}
-while the objects in the unguided experiment are
+%\begin{equation*}
+  %\mathbf{u}_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
+%\end{equation*}
+%while the objects in the unguided experiment are
 
-\begin{equation*}
-  \mathbf{u}_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
-\end{equation*}
+%\begin{equation*}
+  %\mathbf{u}_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
+%\end{equation*}
 %A picture of the unguided experiment environment is given in Fig.~\ref{fig:experiment-env}.

### 2019-05-06 paper.tex
Merged sections

@@
 \begin{abstract}
-  The ActiVis project aims to deliver a system for a mobile device that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
-  To do so, it uses new developments in object detection methods, mobile computing, action generation and human-computer interfacing to interpret the user's surroundings and present useful guidance directions.
-  Our approach to action generation used a Markov Decision Process (MDP) to track the system's state and output the next best location to investigate to find a target object and has been shown to work in principle in~\cite{lock2019active}.
-  This work expands upon that by adding an object detector and adapting the decision-making process accordingly, providing a complete object search and guidance pipeline.
-  The improved ActiVis system was evaluated in a set of experiments and it outperformed the baseline, unguided case.
+  The ActiVis project aims to deliver a mobile system that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
+  For this, it uses new developments in object detection, mobile computing, action generation and human-computer interfacing to interpret the user's surroundings and present effective guidance directions.
+  Our approach to direction generation uses a Markov Decision Process to track the system's state and output the optimal location to investigate and has been shown to work~\cite{lock2019active}.
+  This work adds an object detector and adapts the guidance process accordingly to provide a complete object search and guidance pipeline.
+  The improved ActiVis system was evaluated in a set of experiments and outperforms the baseline, unguided case.
   \keywords{Active vision, vision impairment, object detection}
@@
 
-Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and human controller in Sections~\ref{sec:active-vision} and~\ref{sec:human-controller} respectively.
+Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and controller in Section~\ref{sec:active-vision}.
 The experiments that were conducted in this work and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.
@@
 
-In this case, the error, $e$, is defined as the difference between the desired object and the object currently within view. 
-The implication of adding a human into the loop is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
-However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
+%The error, $e$, is defined as the difference between the desired object and the object currently within view. 
+Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
+However, the challenge is that a person may interpret \emph{u} in any unpredictable way that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
 It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
-%These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}
+The object detector's classification errors, \emph{n}, is added to the feedback loop as a noise signal and affects \emph{K}'s output.
 
-Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector's classification errors that influence the action that \emph{K} generates.
-In our previous work, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
-In this work we do away with that somewhat naive assumption and implement a POMDP that can handle classification uncertainties in object detectors and classifiers.
+In our previous work~cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
+In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
+%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
+This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
+The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
+The design and implementation of this controller are discussed next.
 
-\section{Human Controller}\label{sec:human-controller}
+%\section{Human Controller}\label{sec:human-controller}
 
-The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
-It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
-The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
+%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
+%It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
+%The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
 %A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.
@@
 The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
-Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.
+%Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.
 
@@
 
-\begin{figure}[h]
+\begin{figure}
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
+  \includegraphics[width=0.6\textwidth]{figures/boxplot_time_to_target.png}
   \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
@@
 
-\begin{figure}[h]
+\begin{figure}
   \centering

### 2019-05-06 paper.tex
Merged param sections

@@
 ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to take to reach the target object.
-To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone that generates real-time navigation instructions to guide the user to their target object.
+To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP) on a mobile phone that generates real-time navigation instructions to guide the user to their target object.
 This work makes the following contributions:
@@
 Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and controller in Section~\ref{sec:active-vision}.
-The experiments that were conducted in this work and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.
+The experiments and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.
 
@@
 
-\subsection{Design}
+\subsection{Controller Design}
 
@@
 %$\mathbf{b}$ is updated for every timestep and action-observation pair.
-Each of the POMDP's parameters are discussed next. 
+The POMDP's parameters and training process are discussed next. 
 %This update is done with
@@
 
-\subsubsection{State Space}
+\subsubsection{Parameters}
 
-The state is given by $s = \langle u, n, v \rangle$, where $u, u\in\mathbf{U}$, is the object within view, n the number of search steps taken since the search began and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
-
-\subsubsection{Actions}
+The state is given by $s = \langle u, n, v \rangle$, where $u, u\in\mathbf{U}$, is the object within view, $n$ the number of search steps taken during search and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
 
 The possible actions that dictates the location the mobile device will generate the next waypoint are given by $\mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}$.
-
-\subsubsection{Transitions}
 
@@
 
-\subsubsection{Reward Function}
-
 The reward function encourages the device controller to search for and find the target object by giving it a substantial reward for doing so, while penalising it for every action that does not result in it finding the target object.
@@
 
-\begin{table}
+\begin{table}[h]
   \centering
@@
 \end{table}
-
-\subsubsection{Observations and Observation Matrix}
 
@@
 We found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
-Multiple algorithms have been proposed~\cite{bargiacchi2016dynamic,silver2010monte} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library\footnote{github.com/Svalorzen/AI-Toolbox} to solve the POMDP model.
+In this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library\footnote{github.com/Svalorzen/AI-Toolbox} to solve the POMDP model.
 The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking these points only. 
@@
 To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly.
-A similar approach was used in~\cite{schauerte2012assistive}.
+%A similar approach was used in~\cite{schauerte2012assistive}.
 With this interface and headset, ActiVis is able to describe location of a waypoint to a user in the pan and tilt dimensions.
@@
 This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
-This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
+This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.%~\cite{lin2014microsoft}. 
 The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).

### 2019-05-06 paper.tex
We did it!!

@@
 There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
-The work we present here is part of the ActiVis project that aims to assist people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
+This work is part of the ActiVis project that aims to enable people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
 This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
@@
 
-ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to take to reach the target object.
-To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP) on a mobile phone that generates real-time navigation instructions to guide the user to their target object.
+ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to take to find the target object.
+For this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP) on a mobile phone that generates real-time navigation instructions for the user.
 This work makes the following contributions:
@@
 Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and controller in Section~\ref{sec:active-vision}.
-The experiments and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.
+The experiments and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}.
+The paper is concluded in Section~\ref{sec:conclusion}.
 
@@
 Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}.
-The device uses a feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
-Improvements to feature detectors have made it viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects while providing the same guidance functionality.
+The device uses audio feedback to read out the embedded information or guide the user towards the markers. 
+Improvements to feature detectors have made it viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture.
+%that requires the user to send a photo of their environment to a Mechanical Turk worker who sends the position of the requested object within the picture back to the user. 
 %The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
-An alternative detection approach proposed in~\cite{bigham2010vizwiz} requires the user to send a photo of their environment to a Mechanical Turk worker that sends the position of the requested object within the picture back to the user.
 
 The issue with a marker-based approach is that it requires significant effort to place and maintain them in an environment, which is remedied by markerless systems.
-However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
-The system in~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to help guide a user to the correct location, but the there is significant lag and a reliance on a good internet connection and remote worker being available.
-Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that provides the user with pointing instructions to find an out-of-view object and proved that this is a viable method to search for an object.
-However, this work used barcodes encoded with object information to simulate real objects.
+However, both of these methods use passive guidance approaches that rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
+VizWiz~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to guide a user to the correct location, but the there is significant lag and a reliance on a good internet connection and remote worker being available.
+Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object and showed that this is a viable method of object search.
+However, this work used encoded barcodes to simulate real objects.
 In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.
@@
 
-The ActiVis project's goal is developing a mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
+%The ActiVis project's goal is developing a mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
 %This work focuses on guiding a user towards an object in one static environment and is limited to 2 dimensions (pan and tilt).
 
-A complete system diagram is given in Fig.~\ref{fig:sys-diagram}. 
-This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, but has been modified to incorporate a human within the loop.
+A complete system diagram for Activis is given in Fig.~\ref{fig:sys-diagram}. 
+This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, but has been modified to incorporate a human within the loop.
 
@@
   \centering
-  \includegraphics[width=0.75\textwidth]{figures/control_loop.png}
+  \includegraphics[width=0.7\textwidth]{figures/control_loop.png}
   \caption{The system control loop including a human and the controller.}\label{fig:sys-diagram}
@@
 %The error, $e$, is defined as the difference between the desired object and the object currently within view. 
-Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
+Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives a control signal, \emph{u}, from the controller, \emph{K}. 
 However, the challenge is that a person may interpret \emph{u} in any unpredictable way that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
@@
 
-In our previous work~cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
+In our previous work~\cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
 In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{figures/desk_example.png}
+  \includegraphics[width=0.4\columnwidth]{figures/desk_example.png}
   \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects}\label{fig:openimage}
@@
 
-\begin{table}[h]
+\begin{table}
   \centering
@@
 This is done by having the model explore the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.
-The difficulty of solving POMDPs is that $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
-We found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
-In this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library\footnote{github.com/Svalorzen/AI-Toolbox} to solve the POMDP model.
-The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking these points only. 
+However, $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
+We found this to be the case for our moderately-sized state space size and opted for an approximate method instead.
+We used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point}, as implemented in the AI-Toolbox library\footnote{github.com/Svalorzen/AI-Toolbox}, to solve the POMDP model.
+The PBVI algorithm speeds up the training process by selecting a smaller subset of representative belief points from $\mathbf{b}$ and tracking these points only. 
 Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.
@@
 
-We implemented the object detector and POMDP controller by combining it with an audio interface that provides non-visual guidance instructions onto an Android app.% that can be used by a PwVI by adding .% onto a mobile phone that can generate and provide guidance instructions for a user.
-Non-visual feedback allows the app to be used by PwVI.
+%Non-visual feedback allows the app to be used by PwVI.
 %This was done by combining an audio interface that provides non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
-Each of these aspects and their implementation are discussed here.
+%Each of these aspects and their implementation are discussed here.
 
-\subsubsection{Audio Interface}
+%\subsubsection{Audio Interface}
 
-ActiVis's target audience are PwVI and therefore provides guidance instructions in a non-visual manner that is intuitive and easy to understand. 
-To avoid blocking a user's access to ambient sounds, we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.
+We implemented the object detector and POMDP controller into an Android app and combined it with an audio interface that provides non-visual guidance instructions.
+% that can be used by a PwVI by adding .% onto a mobile phone that can generate and provide guidance instructions for a user.  
+%ActiVis's target audience are PwVI and therefore provides guidance instructions in a non-visual manner that is intuitive and easy to understand. 
+To avoid blocking a user's access to ambient sounds, we use non-intrusive bone-conducting headphones to transmit the audio signals to the user.
 
@@
 To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly.
-%A similar approach was used in~\cite{schauerte2012assistive}.
-With this interface and headset, ActiVis is able to describe location of a waypoint to a user in the pan and tilt dimensions.
+A similar approach was used in~\cite{schauerte2012assistive}.
+%This interface enables ActiVis to describe the location of a waypoint to a user in the pan and tilt dimensions.
 
-\subsubsection{Object Detector}
+%\subsubsection{Object Detector}
 
@@
 This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
-This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.%~\cite{lin2014microsoft}. 
+This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.
 The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
@@
 
-The network was trained with a maximum of 10000 object samples, taken from the OpenImages dataset~\cite{openimages}, for each object class in $\mathbf{U}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
+The network was trained with a maximum of 10000 object samples for each class in $\mathbf{U}$, taken from the OpenImages dataset~\cite{openimages}, with a 60\%/20\%/20\% split for training, validation and testing respectively.
 We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
-With 120 training epochs with 1000 iterations each, we achieved a mAPs of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android. 
+With 120 training epochs with 1000 iterations each, we achieved a mAPs of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android and we used this model to implement an SSD-Lite object detector onto a mobile device.
 %We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
@@
 
-\subsubsection{Action Generator}
+%\subsubsection{Action Generator}
 
-The output from the POMDP model's training process is a policy file that defines the best location to place the next search waypoint based on the device's current state.
+To generate new waypoints, the system uses the policy file output from the POMDP model's training process that defines the best location to place the next search waypoint based on the device's current state.
 This state is tracked by the device throughout the app's runtime by performing object detection and recording the device's previous search locations and previous waypoint positions
-The latter is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
-Each grid square represents a \SI{35}{\degree} angular translation and the grid encompasses a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
+The latter is done by disretising the world into a $6\times6$ grid, each representing a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value.
+%Each grid square represents a \SI{35}{\degree} angular translation and the grid encompasses a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
 This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector. 
-
 When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
@@
 
-Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement. 
-However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences which is not a problem since most offices contain the same basic furniture and objects. 
+Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects.
+%However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences which is not a problem since most offices contain the same basic furniture and objects. 
 The objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects between experiments. 
-The objects in the guided experiment environment are
-
-\begin{equation*}
-  \mathbf{u}_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
-\end{equation*}
-while the objects in the unguided experiment are
-
-\begin{equation*}
-  \mathbf{u}_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
-\end{equation*}
+The objects in the guided experiment environment are $\mathbf{u}_{guided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided experiment are $\mathbf{u}_{unguided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.
 
@@
 The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{developers.google.com/ar/} and text-to-speech enabled. 
+A time limit of 45 seconds was set for each experiment run, which was ended when the target object was found or the time limit was reached, and there was one experiment run per target in the respective environment.
 
@@
 It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
-This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller} where the human acts as both the actuator and controller.
+%This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller} where the human acts as both the actuator and controller.
+In this case, the human acts as both the controller and actuator. 
 The app only reads out the objects upon the user's request by tapping on the screen. 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{figures/control_loop_no_controller.png}
-  \caption{The control loop with the human acting as bot manipulator and controller. }\label{fig:sys-diagram-no-controller}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.4\textwidth]{figures/control_loop_no_controller.png}
+  %\caption{The control loop with the human acting as both manipulator and controller. }\label{fig:sys-diagram-no-controller}
+%\end{figure}
 
-Each participant was verbally informed prior to each experiment what the target object was and they were given 45 seconds to find it and each run was ended when a target was found or the time limit was reached.
-The learning effect was ignored in order to mimic the normal search behaviour described earlier and allow full use of prior knowledge. 
-This process performed once for each object in the experiment set.
+%Each participant was verbally informed prior to each experiment what the target object was.
+%The learning effect was ignored in order to mimic the normal search behaviour described earlier and allow full use of prior knowledge. 
+%This process performed once for each object in the experiment set.
+
+To mimic the normal search behaviour and allow the participant's to use their intuition and prior knowledge, we ignored the learning effect for this experiment and verbally informed them what their target was for each experiment run.
 
@@
 This also isolated the performance measurement to the guidance system alone.
-An experiment run started with the experiment staff selecting the target and was terminated when the target object was found or the 45 second time limit was reached.
-This process performed once for each object in the experiment set.
+An experiment run started with the experiment staff selecting the target.
+%and was terminated when the target object was found or the 45 second time limit was reached.
+%This process performed once for each object in the experiment set.
 
@@
 
-The target acquisition rate (TAR) is the proportion of objects the participants successfully found during an experiment. 
+The target acquisition rate (TAR) is the proportion of objects the participants found during an experiment. 
 For example, a TAR of 0.5 indicates that a participant found the target object in 50\% of searches. 
-Taking each participant's TAR as a datum, we found the unguided case produced a higher average TAR (0.54 vs.
-0.46), meaning that a participant found around 8\% more objects without guidance instructions.
-However, the Kruskal-Wallis (KW) test for non-normal data shows that these results are statistically not significantly different from one another ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR.
+Taking each participant's TAR as a datum, we found the unguided case produced a higher average TAR (0.54 vs. 0.46), meaning that participants found 8\% more objects without guidance instructions.
+However, the Kruskal-Wallis (KW) test for non-normal data shows that these results are statistically not significantly different ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR.
 All the experiment results are summarised in Table~\ref{tab:results}.
@@
 The device displacement was measured in both linear ($x, y, z$) and angular (pan, tilt) dimensions.
-By integrating these data we obtain and compare the total absolute displacement in each dimension.
+Integrating these data, we obtain the total absolute displacement in each dimension.
 These results are plotted in Fig.~\ref{fig:boxplot-displacement}.
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
+  \includegraphics[width=0.7\textwidth]{figures/boxplot_displacement.png}
   \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}

### 2019-05-06 paper.tex
We did it (again)!!

@@
 The device uses audio feedback to read out the embedded information or guide the user towards the markers. 
-Improvements to feature detectors have made it viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture.
+Improvements to feature detectors have made it viable~\cite{redmon2016you} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture.
 %that requires the user to send a photo of their environment to a Mechanical Turk worker who sends the position of the requested object within the picture back to the user. 
@@
 Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
-On the other hand, single-stage models, such as SSD, YOLO and MobileNet~\cite{liu2016ssd,redmon2018yolo,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models.
+On the other hand, single-stage models, such as SSD and MobileNet~\cite{liu2016ssd,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models.
 %MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{figures/boxplot_time_to_target.png}
+  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
   \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/boxplot_displacement.png}
+  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
   \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}

### 2019-05-06 paper.tex
Final minor edits and spelling corrections. Submitted and forgotten about

@@
 There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
-This work is part of the ActiVis project that aims to enable people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
+This work is part of the ActiVis\footnote{lcas.github.io/ActiVis} project that aims to enable people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
 This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
@@
 Object detectors mainly come in 2 flavours: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
-Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
+Between the 2 types, there is a speed-accuracy trade-off, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
 On the other hand, single-stage models, such as SSD and MobileNet~\cite{liu2016ssd,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models.
@@
 %In this case, the state is inferred based on the model parameters and the associated sensor accuracy (if a sensor is 100\% accurate, the state would be directly observable).
-The implication of this is that a POMDP-based agent does not know its state at any point in time, but must infer it based on the known model parameters and sensor accuracy, the object detector's accuracy in this case.
+The implication of this is that a POMDP-based agent does not know its state at any point in time, but must infer it based on the known model parameters and sensor accuracy, which is the object detector's accuracy in this case.
 This state inference relies on a so-called belief meta-state that is updated with additional observations to reflect the likelihood that the agent is in any given state.
@@
 This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
-This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.
-The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
+This model achieves a mean average precision (mAP) of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.
+The full SSD model achieves a slightly higher mAP (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
 %Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.
@@
 We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
-With 120 training epochs with 1000 iterations each, we achieved a mAPs of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android and we used this model to implement an SSD-Lite object detector onto a mobile device.
+With 120 training epochs with 1000 iterations each, we achieved a mAP of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android and we used this model to implement an SSD-Lite object detector onto a mobile device.
 %We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}

### 2019-07-01 paper.tex
Cleared commented code

@@
 \author{J.C. Lock\inst{1} \and
-  G. Cielniak\inst{1} \and
   A.G. Tramontano\inst{2} \and
+  S. Ghidoni\inst{2} \and
   N. Bellotto\inst{1}
@@
 
-%Mobile devices that can detect objects and guide PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing and image processing methods.
 Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}.
@@
 Improvements to feature detectors have made it viable~\cite{redmon2016you} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture.
-%that requires the user to send a photo of their environment to a Mechanical Turk worker who sends the position of the requested object within the picture back to the user. 
-%The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
 
@@
 On the other hand, single-stage models, such as SSD and MobileNet~\cite{liu2016ssd,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models.
-%MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
-%The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects.
-%They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
-%On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
-%These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
-%Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
-%There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
-%MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
-%This leads to model that uses much less memory, but again with a small drop in accuracy.
 
 \section{Active Vision System}\label{sec:active-vision}
-
-%The ActiVis project's goal is developing a mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
-%This work focuses on guiding a user towards an object in one static environment and is limited to 2 dimensions (pan and tilt).
 
@@
 
-%The error, $e$, is defined as the difference between the desired object and the object currently within view. 
 Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives a control signal, \emph{u}, from the controller, \emph{K}. 
@@
 In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
-%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
 This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
@@
 The design and implementation of this controller are discussed next.
-
-%\section{Human Controller}\label{sec:human-controller}
-
-%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
-%It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
-%The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
-%A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.
 
@@
 Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
-%$\mathbf{b}$ is updated for every timestep and action-observation pair.
 The POMDP's parameters and training process are discussed next.
-%This update is done with
-
-%\begin{equation}
-  %b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s), 
-%\end{equation}
-%where $\eta$ is a normalisation factor.
-
-%The state space, reward function and transition matrix are conceptually similar the same as the MDP described in~\cite{lock2019active}. 
-%The major difference is the addition of an observation matrix that defines the probability of being in any given state after making a new observation.
-%In essence, it is a measure of the sensor accuracy, and in this case it describes the object detector's classification accuracy and recall.
-%These parameters are given by the following.
 
@@
 The transition function for this case is $t(s, a, s') = t(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16$.
-
-%\begin{equation*}
-  %t(s, a, s') = t(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16.
-%\end{equation*}
-%An image displaying this relationship can be seen in Fig.~\ref{fig:openimage}.
 
@@
 
-%Non-visual feedback allows the app to be used by PwVI.
-%This was done by combining an audio interface that provides non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
-%Each of these aspects and their implementation are discussed here.
-
-%\subsubsection{Audio Interface}
-
 We implemented the object detector and POMDP controller into an Android app and combined it with an audio interface that provides non-visual guidance instructions.
-% that can be used by a PwVI by adding .% onto a mobile phone that can generate and provide guidance instructions for a user.  
-%ActiVis's target audience are PwVI and therefore provides guidance instructions in a non-visual manner that is intuitive and easy to understand. 
 To avoid blocking a user's access to ambient sounds, we use non-intrusive bone-conducting headphones to transmit the audio signals to the user.
@@
 A similar approach was used in~\cite{schauerte2012assistive}.
-%This interface enables ActiVis to describe the location of a waypoint to a user in the pan and tilt dimensions.
-
-%\subsubsection{Object Detector}
 
@@
 The full SSD model achieves a slightly higher mAP (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
-%Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.
 
@@
 With 120 training epochs with 1000 iterations each, we achieved a mAP of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android and we used this model to implement an SSD-Lite object detector onto a mobile device.
-%We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
-%This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
-%\todo{add mAPs we achived}
-
-%\subsubsection{Action Generator}
 
@@
 The latter is done by disretising the world into a $6\times6$ grid, each representing a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value.
-%Each grid square represents a \SI{35}{\degree} angular translation and the grid encompasses a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
 This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector. 
@@
 We conducted an additional set of experiments with an alternative system that relies on a user's intuition and prior knowledge to generate actions instead, to act as a baseline measurement for our system's results.
-%This alternative system does not provide any guidance instructions to the user.
-%Instead, it provides the user with raw observations from the object classifier and relies on the user's intuition and prior knowledge to generate actions. 
-%The goal of both the guided and unguided experiment cases were to find an object within a static environment.
 
 Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects.
-%However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences which is not a problem since most offices contain the same basic furniture and objects. 
-The objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects between experiments. 
+To minimise any cross-experiment learning effects, 2 different sets of objects were used for each experiment and any objects that occurred in both experiments were placed at different positions for each experiment.
 The objects in the guided experiment environment are $\mathbf{u}_{guided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided experiment are $\mathbf{u}_{unguided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.
@@
 It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
-%This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller} where the human acts as both the actuator and controller.
 In this case, the human acts as both the controller and actuator. 
@@
 When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.
-
-%\begin{figure}
-  %\centering
-  %\includegraphics[width=0.4\textwidth]{figures/control_loop_no_controller.png}
-  %\caption{The control loop with the human acting as both manipulator and controller. }\label{fig:sys-diagram-no-controller}
-%\end{figure}
-
-%Each participant was verbally informed prior to each experiment what the target object was.
-%The learning effect was ignored in order to mimic the normal search behaviour described earlier and allow full use of prior knowledge. 
-%This process performed once for each object in the experiment set.
 
@@
 An experiment run started with the experiment staff selecting the target.
-%and was terminated when the target object was found or the 45 second time limit was reached.
-%This process performed once for each object in the experiment set.
-
-%\subsection{Environment Setup}
-
-%The environment and the object placement within it for both experiments was modelled on a typical office.
-%Measures were taken to ensure that both office environments were unique in layout and object placement. 
-%However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, which is not a problem since most offices contain the same basic furniture and objects. 
-%These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
-%The objects in the guided experiment environment are
-
-%\begin{equation*}
-  %\mathbf{u}_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
-%\end{equation*}
-%while the objects in the unguided experiment are
-
-%\begin{equation*}
-  %\mathbf{u}_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
-%\end{equation*}
-%A picture of the unguided experiment environment is given in Fig.~\ref{fig:experiment-env}.
-
-%\begin{figure}
-  %\centering
-  %\includegraphics[width=0.7\textwidth]{figures/environment.png}
-  %\caption{A picture of the experiment setup. }\label{fig:experiment-env}
-%\end{figure}
 
@@
 \subsection{Target Acquisition}
-
-%We set an upper time limit for each object search run of 45 seconds.
-%When this upper threshold was reached, the search was recorded as a failure and the next run was started.
 
@@
 
-%\todo{Should I add CDF?}
 The time it takes to find a target object is an important indicator of system performance, where less time indicates a shorter search time and increased performance.
-The data for the search times for each experiment are shown in Fig.~\ref{fig:boxplot-time}.%, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.
+The data for the search times for each experiment are shown in Fig.~\ref{fig:boxplot-time}.
 
@@
 
-%\begin{figure}
-  %\centering
-  %\includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
-  %\caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
-%\end{figure}
-
-%To compensate for the different numbers of targets found per participant and for each experiment setup, we average each participant's results, giving us 10 samples per experiment. 
 From Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
 This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
-%These results are summarised in Table~\ref{tab:results}. 
-%With this 27\% reduction in total time spent searching for a target object, we can conclude that a user benefits from using our smart guidance system as opposed to relying on a simple object reader. 
-%This is supported by the CDFs in Fig.~\ref{fig:cum-time} that show that \todo{Discuss the less number of objects found and how it is not statistically signioficatn. Perhaps show it in CDF}
 
@@
 To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
-In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user.%, enhancing user experience and improving ease of use.
-%\todo{maybe cite paper that says less exertion is good}.
+In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user.
 
@@
 These results are plotted in Fig.~\ref{fig:boxplot-displacement}.
-
-%\begin{figure}
-  %\centering
-  %\includegraphics[width=0.7\textwidth]{figures/boxplot_angle.png}
-  %\caption{A set of boxplots comparing the angular distance the device travelled for each experiment. }\label{fig:boxplot-angle}
-%\end{figure}
-
-%\begin{figure}
-  %\centering
-  %\includegraphics[width=0.7\textwidth]{figures/boxplot_dist.png}
-  %\caption{A set of boxplots comparing the distance the device travelled for each experiment. }\label{fig:boxplot-dist}
-%\end{figure}
 

### 2019-07-01 paper.tex
Fixed some review comments

@@
 However, both of these methods use passive guidance approaches that rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
-VizWiz~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to guide a user to the correct location, but the there is significant lag and a reliance on a good internet connection and remote worker being available.
+VizWiz~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to guide a user to the correct location, but there is significant lag and a reliance on a good internet connection and remote worker being available.
 Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object and showed that this is a viable method of object search.
@@
 A complete system diagram for Activis is given in Fig.~\ref{fig:sys-diagram}. 
-This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, but has been modified to incorporate a human within the loop.
+This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, and drive the output to some reference, $r$, but has been modified to incorporate a human within the loop.
+$r$ in this case is a camera image containing the target object.
 
@@
 This state is tracked by the device throughout the app's runtime by performing object detection and recording the device's previous search locations and previous waypoint positions
-The latter is done by disretising the world into a $6\times6$ grid, each representing a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value.
+The latter is done by discretising the world into a $6\times6$ grid, each representing a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value.
 This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector. 
@@
 We implemented this system on an Android app and tested it with a group of 10 participants to evaluate its effectiveness compared to a baseline, unguided case that only uses the object detector and relies on the human to generate the search path.
-The key results from these experiment is that the guidance system improved the participants' target-searching performance, reducing the total search time and overall camera manipulation effort required when compared to a base case.
+The key results from these experiments are that the guidance system improved the participants' target-searching performance, reducing the total search time and overall camera manipulation effort required when compared to a base case.
 However, the participants were able to find 8\% more objects on average in the unguided case, but this result was found to be statistically insignificant. 

### 2019-07-02 paper.tex
Changed spacing in table, explanation on r, removed commented line

@@
 This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, and drive the output to some reference, $r$, but has been modified to incorporate a human within the loop.
-$r$ in this case is a camera image containing the target object.
+$r$ in this case is the target object.
 
@@
 In our previous work~\cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
-In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
+In this work we do away with that somewhat naive assumption and replace the MDP controller with a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers.
 This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
@@
 A POMDP is an extension to the MDP model that allows it to handle cases where the state is not directly observable, allowing it to be used in more realistic scenarios. 
-%In this case, the state is inferred based on the model parameters and the associated sensor accuracy (if a sensor is 100\% accurate, the state would be directly observable).
 The implication of this is that a POMDP-based agent does not know its state at any point in time, but must infer it based on the known model parameters and sensor accuracy, which is the object detector's accuracy in this case.
@@
 We encoded 16 objects, including a `nothing' object where the detector does not see anything of interest, into the controller and object detector.
-These objects are defined as
+These objects given by
 

### 2019-07-02 paper.tex
Added todo to address comparrisson with visapp work issue, added sentence to previous work section clarifying that the visapp work was proof-of-concept and experiments reflect that

@@
 Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object and showed that this is a viable method of object search.
-However, this work used encoded barcodes to simulate real objects.
-In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.
+However, that work moved to establish that an MDP-based controller is indeed a viable to generate guidance instructions and reduced variability by using encoded barcodes to simulate real objects and on-screen prompts to present the guidance instructions.
+In this work, we are expanding the control model and replacing the barcodes with real objects and providing audio guidance, thereby providing a complete object detection and guidance pipeline for people with vision impairments.
 
@@
 
+\todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}
+
 \section{Conclusion}\label{sec:conclusion}

### 2019-07-02 paper.tex
Added rewards from visapp, explained how I came up with it

@@
 
-% Package for todo command
-\usepackage{xcolor}
-
-\newcommand\todo[1]{\textcolor{red}{#1}}
+\usepackage{todonotes}
 
@@
 Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) or when it exceeds some search length threshold denoted by $n_{\max}$.
-The rewards are summarised in Table~\ref{tab:rewards}.
+The reward values were selected based on lessons learned during the implementation of the MDP model and the rewards for both that and this work are summarised in Table~\ref{tab:rewards}.
 
@@
   \caption{The reward function for the POMDP. }\label{tab:rewards}
-  \begin{tabular}{p{3cm}p{1cm}}
+  \begin{tabular}{p{3cm}p{2cm}p{2cm}}
     \toprule
-    $r(o = o_{target})$ & 10000 \\ \midrule
-    $r(v = \textrm{true})$  & -75 \\ \midrule
-    $r(n > n_{\max})$ & -75 \\ \midrule
-    otherwise $r(\cdot)$ & -100  \\ \midrule
+    Reward condition        & POMDP  & MDP   \\ \midrule
+    $r(o = o_{target})$     & 10000  & 10000 \\ 
+    $r(v = \textrm{true})$  & -75    & -10   \\
+    $r(n > n_{\max})$       & -75    & -10   \\
+    otherwise $r(\cdot)$    & -100   & -1    \\
     \bottomrule
@@
 \todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}
+\todo{Make sure paper fits into 10+1 page limit for content and references}
 

### 2019-07-02 paper.tex
Mentioned VISAPP results. However, I have doubts that we should use it, it might only confuse the reader since the experiments differ completely

@@
 This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
+These results compare favourably with those collected from experiments performed with this system's previous iteration where an average time to target of 31s was recorded~\cite{lock2019active}. 
+However, it should be noted that the system implementation and experiment design for this work is significantly different and this comparison is symbolic more than it is indicative of major improvement.
+\todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}
 
@@
 
-\todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}
 \todo{Make sure paper fits into 10+1 page limit for content and references}

### 2019-07-04 paper.tex
a few fixes and comments

@@
 \usepackage{todonotes}
+
+\usepackage{soul}
+\DeclareRobustCommand{\tofix}[1]{{\sethlcolor{yellow}\hl{[#1]}}}
 
@@
 \authorrunning{Jacobus C. Lock et. al.}
-\institute{University of Lincoln, Lincoln, UK \and
-  Universit\`{a} degli studi di Padova, Italy
+\institute{School of Computer Science, University of Lincoln, United Kingdom \and
+ Department of Information Engineering, University of Padova, Italy
 }
@@
 There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
-This work is part of the ActiVis\footnote{lcas.github.io/ActiVis} project that aims to enable people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
+This work is part of the ActiVis\footnote{http://lcas.github.io/ActiVis} project that aims to enable people with vision impairments to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
 This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/system_use.png}
-  \caption{The system in use during an experiment with a blindfolded participant. }\label{fig:system-in-use}
+  \includegraphics[width=0.45\textwidth]{figures/system_use.png} \hfil
+  \includegraphics[width=0.45\textwidth]{figures/system_use.png}
+  \caption{The system in use during an experiment with a blindfolded participant. \tofix{can you add another image with (most of) the objects? maybe arranged in a grid} }\label{fig:system-in-use}
 \end{figure}
@@
 This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, and drive the output to some reference, $r$, but has been modified to incorporate a human within the loop.
-$r$ in this case is the target object.
+In this case, $r$ is the target object.
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
-  \includegraphics[width=0.4\columnwidth]{figures/desk_example.png}
-  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects}\label{fig:openimage}
+  \includegraphics[width=0.45\columnwidth]{figures/desk_example.png} \hfil
+  \includegraphics[width=0.45\columnwidth]{figures/desk_example.png}
+  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects. \tofix{add one more image, different from VISAPP though}}\label{fig:openimage}
 \end{figure}
@@
 
-We encoded 16 objects, including a `nothing' object where the detector does not see anything of interest, into the controller and object detector.
-These objects given by
-
+We encoded 16 objects, including a `nothing' object where the detector does not see anything of interest, into the controller and object detector:
 \begin{equation*}
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
   \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
-  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
+  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment.\tofix{Half the height of the image.
+You can also put it together with Fig.~4 to save space.}}\label{fig:boxplot-displacement}
 \end{figure}
@@
 The next steps for the project are to refine and expand the object detector to include objects from other environments.
+\tofix{that's it?
+a little bit more imagination...
+what about user- adaptation?
+different interface, maybe with different audio, voice, vibration etc.?
+evaluation with larger pool of VI participants?
+It doesn't mean you have to do it, but it gives ideas for future improvements and research projects.}
 

### 2019-07-04 paper.tex
a few revisions to asbtract and sec 1

@@
   For this, it uses new developments in object detection, mobile computing, action generation and human-computer interfacing to interpret the user's surroundings and present effective guidance directions.
-  Our approach to direction generation uses a Markov Decision Process to track the system's state and output the optimal location to investigate and has been shown to work~\cite{lock2019active}.
-  This work adds an object detector and adapts the guidance process accordingly to provide a complete object search and guidance pipeline.
-  The improved ActiVis system was evaluated in a set of experiments and outperforms the baseline, unguided case.
+  Our approach to direction generation uses a Markov Decision Process to track the system's state and output the optimal location to be investigated.
+  This system includes an object detector and an audio-based guidance interface to provide a complete active search pipeline.
+  The ActiVis system was evaluated in a set of experiments showing better performance than a simpler unguided case.
   \keywords{Active vision, vision impairment, object detection}
@@
 There are an estimated half a billion people that live with mild to severe vision impairment or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
-There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
-This work is part of the ActiVis\footnote{http://lcas.github.io/ActiVis} project that aims to enable people with vision impairments to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
-This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
-This project expands upon concepts proposed in~\cite{bellotto2013,lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.
+There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible, and improvements in modern computing power and image processing capabilities have made this easier.
+This work is part of the ActiVis\footnote{http://lcas.github.io/ActiVis} project, which aims to enable people with vision impairments to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
+Our solution is inspired by active vision research~\cite{bajcsy2017}, but it replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand, as pictured in Fig.~\ref{fig:system-in-use}.
+This paper expands upon concepts proposed in~\cite{bellotto2013,lock2017portable} and extends the concept presented in~\cite{lock2019active} with a fully working system.
 
@@
 
-ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to take to find the target object.
-For this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP) on a mobile phone that generates real-time navigation instructions for the user.
-This work makes the following contributions:
+ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to find the target object.
+For this, we expanded upon our previous work and implemented a Partially Observable Markov Decision Process (POMDP) on a mobile phone that generates real-time navigation instructions for the user.
+The current paper includes the following main contributions:
 
 \begin{itemize}
-  \item a controller that enables object search and guidance on a mobile phone;
-  \item a complete system pipeline that includes interfacing, object detection and human control;
+  \item a new controller that enables object search and guidance on a mobile phone;
+  \item a complete system pipeline that includes audio interface, object detection and human control;
   \item experiments that evaluate the efficacy of the proposed system.
@@
 We found this to be the case for our moderately-sized state space size and opted for an approximate method instead.
-We used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point}, as implemented in the AI-Toolbox library\footnote{github.com/Svalorzen/AI-Toolbox}, to solve the POMDP model.
+We used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point}, as implemented in the AI-Toolbox library\footnote{http://github.com/Svalorzen/AI-Toolbox}, to solve the POMDP model.
 The PBVI algorithm speeds up the training process by selecting a smaller subset of representative belief points from $\mathbf{b}$ and tracking these points only. 
@@
 The other 8 participants were blindfolded to simulate blindness. 
-The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{developers.google.com/ar/} and text-to-speech enabled. 
+The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{http://developers.google.com/ar/} and text-to-speech enabled. 
 A time limit of 45 seconds was set for each experiment run, which was ended when the target object was found or the time limit was reached, and there was one experiment run per target in the respective environment.
@@
 
+\paragraph{{\bf Acknowledgements.}}\label{sec:acknowledge}
+This research is partly supported by a Google Faculty Research Award (Winter 2015).
+\tofix{any charity directly involved in the experiments?}
+
 \bibliographystyle{splncs04}

### 2019-07-05 paper.tex
revised sec 2

@@
 The device uses audio feedback to read out the embedded information or guide the user towards the markers. 
-Improvements to feature detectors have made it viable~\cite{redmon2016you} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture.
+While improvements to feature detectors have made it viable to replace markers with real objects~\cite{redmon2016you}, an alternative guidance approach is proposed in VizWiz~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and guide towards the desired object within a user-provided picture.
 
@@
 VizWiz~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to guide a user to the correct location, but there is significant lag and a reliance on a good internet connection and remote worker being available.
-Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object and showed that this is a viable method of object search.
-However, that work moved to establish that an MDP-based controller is indeed a viable to generate guidance instructions and reduced variability by using encoded barcodes to simulate real objects and on-screen prompts to present the guidance instructions.
-In this work, we are expanding the control model and replacing the barcodes with real objects and providing audio guidance, thereby providing a complete object detection and guidance pipeline for people with vision impairments.
+Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object, showing that this is a viable method for object search.
+However, that work used QR-codes to simulate real objects and on-screen prompts to present the guidance instructions.
+In this paper we expand the control model, replacing the QR-codes with real objects and providing audio guidance, thereby implementing a complete object detection and guidance pipeline for people with vision impairments.
 
-Object detectors mainly come in 2 flavours: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
-Between the 2 types, there is a speed-accuracy trade-off, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
-On the other hand, single-stage models, such as SSD and MobileNet~\cite{liu2016ssd,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models.
+Object detectors can be broadly classified in two-stage models, which use an external algorithm to select regions of interest where to perform object inference~\cite{ren2015faster}, and single-stage models, which generate multiple windows of different sizes and checks each window for any objects.
+Between these two classes, there is a speed-accuracy trade-off, where the two-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
+On the other hand, single-stage models, such as SSD and MobileNet~\cite{liu2016ssd,howard2017mobilenet}, produce less accurate results but require significantly less parameters and FLOPS to perform object inference than the two-stage models.
 
@@
 
-A complete system diagram for Activis is given in Fig.~\ref{fig:sys-diagram}. 
+A complete system diagram for ActiVis is given in Fig.~\ref{fig:sys-diagram}. 
 This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, and drive the output to some reference, $r$, but has been modified to incorporate a human within the loop.

### 2019-07-05 paper.tex
Added new suggested figures

--- 2019-07-04 paper.tex
@@
   \includegraphics[width=0.45\textwidth]{figures/system_use.png} \hfil
-  \includegraphics[width=0.45\textwidth]{figures/system_use.png}
+  \includegraphics[width=0.45\textwidth]{figures/object_grid/grid.png}
   \caption{The system in use during an experiment with a blindfolded participant. \tofix{can you add another image with (most of) the objects? maybe arranged in a grid} }\label{fig:system-in-use}
@@
   \centering
-  \includegraphics[width=0.45\columnwidth]{figures/desk_example.png} \hfil
-  \includegraphics[width=0.45\columnwidth]{figures/desk_example.png}
-  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects. \tofix{add one more image, different from VISAPP though}}\label{fig:openimage}
+  \includegraphics[width=0.35\columnwidth]{figures/desk_example.png} \hfil
+  \includegraphics[width=0.55\columnwidth]{figures/kitchen_example_thicc.png}
+  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects.}\label{fig:openimage}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
-  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
+  \includegraphics[width=1.0\textwidth]{figures/boxplot_combined.png}
+  \caption{A set of boxplots comparing the total linear and angular displacements, as well as the time to target for each experiment. }\label{fig:boxplot-time}
 \end{figure}
@@
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
-  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment.\tofix{Half the height of the image.
+%\begin{figure}[t]
+  %\centering
+  %\includegraphics[width=0.6\textwidth]{figures/boxplot_displacement.png}
+  %\caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment.\tofix{Half the height of the image.
 You can also put it together with Fig.~4 to save space.}}\label{fig:boxplot-displacement}
-\end{figure}
+%\end{figure}
 

### 2019-07-05 paper.tex

@@
   For this, it uses new developments in object detection, mobile computing, action generation and human-computer interfacing to interpret the user's surroundings and present effective guidance directions.
-  Our approach to direction generation uses a Markov Decision Process to track the system's state and output the optimal location to be investigated.
+  Our approach to direction generation uses a Partially Observable Markov Decision Process (POMDP) to track the system's state and output the optimal location to be investigated.
   This system includes an object detector and an audio-based guidance interface to provide a complete active search pipeline.
@@
 VizWiz~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to guide a user to the correct location, but there is significant lag and a reliance on a good internet connection and remote worker being available.
-Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object, showing that this is a viable method for object search.
+Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing a Markov Decision Process (MDP) that gives the user pointing instructions to find an out-of-view object, showing that this is a viable method for object search.
 However, that work used QR-codes to simulate real objects and on-screen prompts to present the guidance instructions.
@@
 A complete system diagram for ActiVis is given in Fig.~\ref{fig:sys-diagram}. 
-This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, and drive the output to some reference, $r$, but has been modified to incorporate a human within the loop.
-In this case, $r$ is the target object.
+This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, $e$, and drive the output to some reference, $r$.
+In our case, the system incorporates a human within the loop; $r$ is the target object and $y$ is the actual observation of the mobile phone's camera.
 
@@
 
-Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives a control signal, \emph{u}, from the controller, \emph{K}. 
-However, the challenge is that a person may interpret \emph{u} in any unpredictable way that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
-It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
-The object detector's classification errors, \emph{n}, is added to the feedback loop as a noise signal and affects \emph{K}'s output.
+Adding a human into the loop means to have an additional block, $H$, representing a human that receives a control signal, $u$, from the controller, $K$. 
+However, the challenge is that a person may interpret $u$ in some unpredictable way, resulting in the signal $u*$ that points the camera, $P$, to a new object observation,~$y$.
+It is therefore important to design $K$ to be robust enough to accommodate different user habits and limitations, ensuring that $u*$ tracks $u$ as closely as possible. 
+The object detector's classification errors, $n$, is added to the feedback loop as a noise signal that affects $K$'s output.
 
-In our previous work~\cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
-In this work we do away with that somewhat naive assumption and replace the MDP controller with a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers.
-This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
+In our previous work~\cite{lock2019active}, we assumed a perfect object classifier and solved the problem using an MDP.
+In this paper we remove that assumption and replace the MDP with a POMDP-based controller that can handle uncertainties in the object detection and classification. 
+Our new controller works by generating a trail of virtual waypoints for the user to point the camera towards, which eventually leads to the target object.
 The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
@@
 
-A POMDP is an extension to the MDP model that allows it to handle cases where the state is not directly observable, allowing it to be used in more realistic scenarios. 
-The implication of this is that a POMDP-based agent does not know its state at any point in time, but must infer it based on the known model parameters and sensor accuracy, which is the object detector's accuracy in this case.
-This state inference relies on a so-called belief meta-state that is updated with additional observations to reflect the likelihood that the agent is in any given state.
+A POMDP is an extension of the MDP that handles cases where the state is not directly observable, allowing it to be used in more realistic scenarios. 
+The implication of this is that a POMDP-based agent does not know its state at any point in time, but must infer it based on the known model parameters and sensor accuracy, which in our case is the object detector's accuracy.
+This state inference relies on a so-called {\em belief meta-state}, which is updated with additional observations to reflect the likelihood that the agent is in any given state.
 The belief state is fully observable by the agent and can be used to infer the mobile device's current state and generate the next action.
 
-A POMDP model is represented by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$, after executing action $a$, $a \in \mathbf{A}$, and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
-$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
-Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.
+A POMDP model is described by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$ (where $s, s' \in \mathbf{S}$) after executing action $a$ (where $a \in \mathbf{A}$), and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
+$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making observation $\omega$ (where $\omega \in \mathbf{\Omega}$) when in state $s$ after executing action $a$.
+\tofix{sure about this?
+I think the observation is before the action...}
+Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards, which affects the model's convergence rate.
 The POMDP's parameters and training process are discussed next.
@@
 
-The state is given by $s = \langle u, n, v \rangle$, where $u, u\in\mathbf{U}$, is the object within view, $n$ the number of search steps taken during search and a binary variable $v$ that tracks the uniqueness of a waypoint's position for the search.
+The state is given by $s = \langle u, n, v \rangle$, where $u\in\mathbf{U}$ is the object within view, $n$ the number of search steps taken during the search and $v$ is a binary variable that tracks the uniqueness of a waypoint's position for the search.
 
-The possible actions that dictates the location the mobile device will generate the next waypoint are given by $\mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}$.
+The possible actions that dictates the location where the mobile device will generate the next waypoint are given by $\mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}$.
 
-$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for a limited number of objects in terms of the actions in $\mathbf{A}$ from the OpenImages~\cite{openimages} dataset. 
+$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for a limited number of objects, in terms of the actions $\mathbf{A}$, from the OpenImages~\cite{openimages} dataset. 
 For example, by iterating over the images containing the objects of interest, we can see that the object `monitor' is located above (i.e.
-UP) the object `keyboard' in 16\% of images containing both objects (see Fig.~\ref{fig:openimage}).
+UP) the object `keyboard' in 16\% of the images containing both objects (see Fig.~\ref{fig:openimage}).
 The transition function for this case is $t(s, a, s') = t(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16$.
@@
 
-The reward function encourages the device controller to search for and find the target object by giving it a substantial reward for doing so, while penalising it for every action that does not result in it finding the target object.
-Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) or when it exceeds some search length threshold denoted by $n_{\max}$.
-The reward values were selected based on lessons learned during the implementation of the MDP model and the rewards for both that and this work are summarised in Table~\ref{tab:rewards}.
+The reward function encourages the device controller to search for the target object by giving a substantial reward if the object is found, while penalising the controller for every action that does not result in a successful object detection.
+Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) or when it exceeds some search-length threshold denoted by $n_{\max}$.
+The reward values were empirically determined starting from the implementation of our previous MDP model~\cite{lock2019active}, the rewards of which are summarised in Table~\ref{tab:rewards} together with the new ones.
+\tofix{can you explain why the last reward (otherwise) is much bigger than before, even bigger than the -75 rewards?}
 
@@
     \toprule
-    Reward condition        & POMDP  & MDP   \\ \midrule
+    Reward condition        & POMDP  & MDP~\cite{lock2019active}   \\ \midrule
     $r(o = o_{target})$     & 10000  & 10000 \\ 
@@
 
-The state observations are identical to the states that the mobile device can enter. 
+The state observations are identical to the states that the mobile device can enter into. 
 In this case, however, uncertainty is introduced into the observation by the object detector.
-Previous search locations and search time are fully observable here, since they can be tracked by the mobile device.
+Instead, the previous search locations and search time are fully observable, since they can be tracked by the mobile device.
 $\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector. 
-These values were found by performing a set of classifier tests on the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$.
+These values were found by performing a set of classification tests with the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$.
 
@@
 
+\tofix{check all references to use correct information and full list of authors (suggest to use manual input on tools like JabRef)}
 \bibliographystyle{splncs04}

### 2019-07-05 paper.tex
revised sec 3

@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figures/system_use.png} \hfil
-  \includegraphics[width=0.45\textwidth]{figures/object_grid/grid.png}
+  \includegraphics[height=4cm]{figures/system_use.png} \hfil
+  \includegraphics[height=4cm]{figures/object_grid/grid.png}
   \caption{The system in use during an experiment with a blindfolded participant. \tofix{can you add another image with (most of) the objects? maybe arranged in a grid} }\label{fig:system-in-use}
@@
 A POMDP model is described by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$ (where $s, s' \in \mathbf{S}$) after executing action $a$ (where $a \in \mathbf{A}$), and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
-$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making observation $\omega$ (where $\omega \in \mathbf{\Omega}$) when in state $s$ after executing action $a$.
+$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making observation $o \in \mathbf{\Omega}$ when in state $s$ after executing action $a$.
 \tofix{sure about this?
@@
 
-The state is given by $s = \langle u, n, v \rangle$, where $u\in\mathbf{U}$ is the object within view, $n$ the number of search steps taken during the search and $v$ is a binary variable that tracks the uniqueness of a waypoint's position for the search.
+The state is given by $s = \langle u, n, v \rangle$, where $u$ is the object within view, $n$ is the number of search steps taken during the search and $v$ is a binary variable indicating whether a waypoint has been visited or not.
 
@@
   \centering
-  \includegraphics[width=0.35\columnwidth]{figures/desk_example.png} \hfil
-  \includegraphics[width=0.55\columnwidth]{figures/kitchen_example_thicc.png}
-  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects.}\label{fig:openimage}
+  \includegraphics[height=4cm]{figures/desk_example.png} \hfil
+  \includegraphics[height=4cm]{figures/kitchen_example_thicc.png}
+  \caption{Images from the OpenImage dataset~\cite{openimages} containing some typical objects.}\label{fig:openimage}
 \end{figure}
@@
 $\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector.
-These values were found by performing a set of classification tests with the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$.
+These values were found by performing a set of classification tests with the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$. \tofix{you mean $\mathbf{O}$?}
 
@@
 
-We encoded 16 objects, including a `nothing' object where the detector does not see anything of interest, into the controller and object detector:
+We encoded 15+1 objects into the current system, including a `nothing' item in case the detector does not see anything of interest:
 \begin{equation*}
@@
 
-\noindent We set $n_{\max}$ to 12 waypoints, after which the agent gets penalised for every additional waypoint it generates that does not lead to the target object. 
+\noindent We set $n_{\max}$ to 11 waypoints, after which the agent gets penalised for every additional waypoint it generates that does not lead to the target object. 
 This results in a total of 352 reachable states ($n_{states} = 16\times11\times2$), with any state containing the target object acting as a terminal state.
 
-The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that the controller can use to produce the optimal waypoint locations.
-This is done by having the model explore the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.
+The POMDP model is trained to generate a policy that contains the optimal belief-action mapping, which the controller can use to produce the optimal waypoint locations.
+This is done by the model exploring the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.
 However, $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
-We found this to be the case for our moderately-sized state space size and opted for an approximate method instead.
-We used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point}, as implemented in the AI-Toolbox library\footnote{http://github.com/Svalorzen/AI-Toolbox}, to solve the POMDP model.
+This was the case for our moderately-sized state space, so we opted for an approximate method instead, using the Point-Based Value Iteration~(PBVI) algorithm~\cite{pineau2003point} implemented in the AI-Toolbox library\footnote{http://github.com/Svalorzen/AI-Toolbox}.
 The PBVI algorithm speeds up the training process by selecting a smaller subset of representative belief points from $\mathbf{b}$ and tracking these points only. 
@@
 
-We implemented the object detector and POMDP controller into an Android app and combined it with an audio interface that provides non-visual guidance instructions.
-To avoid blocking a user's access to ambient sounds, we use non-intrusive bone-conducting headphones to transmit the audio signals to the user.
+We implemented the object detector and the POMDP controller in an Android app and combined it with an audio interface that provides non-visual guidance instructions.
+We use non-intrusive bone-conducting headphones to transmit the audio signals to the user without blocking other ambient sounds.
 
+\subsubsection{Audio Interface}
 To describe the waypoints' pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
 However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
-To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly.
+To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency, respectively~\cite{blauert1997spatial}, and adjust the sound source's pitch accordingly.
 A similar approach was used in~\cite{schauerte2012assistive}.
 
-SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
+\subsubsection{Object Detector}
+To recognise objects we used SSD-Lite, which is a single-stage object detection and classification network based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
 This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
-This model achieves a mean average precision (mAP) of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.
+This model achieves a mean average precision~(mAP) of 0.22 with 4.3M parameters and 0.8B~FLOPS on the COCO dataset~\cite{li2018tinydsod}.
 The full SSD model achieves a slightly higher mAP (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
 
-The network was trained with a maximum of 10000 object samples for each class in $\mathbf{U}$, taken from the OpenImages dataset~\cite{openimages}, with a 60\%/20\%/20\% split for training, validation and testing respectively.
+The network was trained with a maximum of 10,000 object samples for each class in $\mathbf{U}$, taken from the OpenImages dataset~\cite{openimages}, with a 60-20-20\% split for training, validation and testing respectively.
 We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
-With 120 training epochs with 1000 iterations each, we achieved a mAP of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android and we used this model to implement an SSD-Lite object detector onto a mobile device.
+Training for 120 epochs, with 1000 iterations each, we achieved a mAP of 0.16 on this dataset and produced a TensorFlow Lite model that is Android-compatible.
+We used this model to finally implement our SSD-Lite object detector on the mobile device.
 
-To generate new waypoints, the system uses the policy file output from the POMDP model's training process that defines the best location to place the next search waypoint based on the device's current state.
-This state is tracked by the device throughout the app's runtime by performing object detection and recording the device's previous search locations and previous waypoint positions
-The latter is done by discretising the world into a $6\times6$ grid, each representing a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value.
-This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector. 
-When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
-The controller uses $\omega$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
-The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.\ `UP' output would result in a waypoint being placed one grid square above the grid square within view.
+\subsubsection{Waypoint Generation}
+To search the target object, the system uses the policy file from the POMDP training process, which defines the best location of next waypoint based on the device's current state.
+This state is tracked by the device throughout the app's runtime by performing object detection and recording the previous search locations and waypoint positions.
+The latter are obtained by discretising the world into a $6\times6$ grid, where each cell represents a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value when visited.
+This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation $o$ is generated by the object detector. 
+When the device makes a new observation, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
+The controller uses $o$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
+The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.
+an `UP' output would result in a waypoint being placed one grid square above the current view.
+\tofix{double-check all the quantities an definitions in this section (i.e. states, observations, etc.) are correct, because some were a little mixed-up...}
 
@@
 The time it takes to find a target object is an important indicator of system performance, where less time indicates a shorter search time and increased performance.
-The data for the search times for each experiment are shown in Fig.~\ref{fig:boxplot-time}.
+The data for the search times for each experiment are shown in Fig.~\ref{fig:boxplots}.
 
@@
   \includegraphics[width=1.0\textwidth]{figures/boxplot_combined.png}
-  \caption{A set of boxplots comparing the total linear and angular displacements, as well as the time to target for each experiment. }\label{fig:boxplot-time}
+  \caption{A set of boxplots comparing the total linear and angular displacements, as well as the time to target for each experiment. }\label{fig:boxplots}
 \end{figure}
 
-From Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
+From Fig.~\ref{fig:boxplots}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
 This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
@@
 Integrating these data, we obtain the total absolute displacement in each dimension.
-These results are plotted in Fig.~\ref{fig:boxplot-displacement}.
+These results are plotted in Fig.~\ref{fig:boxplots}.
 

### 2019-07-05 paper.tex
revised sec 4

@@
 We use non-intrusive bone-conducting headphones to transmit the audio signals to the user without blocking other ambient sounds.
+The app run in real-time on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{http://developers.google.com/ar/}.% and text-to-speech enabled.
 
@@
 
-Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects.
-To minimise any cross-experiment learning effects, 2 different sets of objects were used for each experiment and any objects that occurred in both experiments were placed at different positions for each experiment.
-The objects in the guided experiment environment are $\mathbf{u}_{guided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided experiment are $\mathbf{u}_{unguided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.
+Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects (e.g.
+door, desk).
+Also, to minimise any cross-experiment learning effects, two different sets of objects were used for each experiment.
+If any (medium-small) objects occurred in both experiments, they were placed at different positions.
+In particular, the objects in the guided case experiment are $\mathbf{U}_{g} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided case are $\mathbf{U}_{ng} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.
 
 We recruited 10 participants (8 male, 2 female; average age 29.2 years) for the experiments, including 2 legally blind participants. 
-The other 8 participants were blindfolded to simulate blindness. 
-The app was run on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{http://developers.google.com/ar/} and text-to-speech enabled. 
-A time limit of 45 seconds was set for each experiment run, which was ended when the target object was found or the time limit was reached, and there was one experiment run per target in the respective environment.
+The other 8 participants were blindfolded. 
+A time limit of 45 seconds was set for each experiment run, which ended either by finding the target object or reaching the time limit.
+There was one experiment run per target in the respective environment. \tofix{not clear here: how many object searches were done by each participant in the guided and unguided cases?}
 
@@
 
-The goal of this experiment is to mimic a typical person with healthy eyesight's search behaviour. 
-In such a scenario, a person would see the objects currently within their field of view and use their prior knowledge and intuition to make a decision on where to look next.
-For example, a person in bathroom facing the basin after washing their hands is unlikely to find a hand dryer placed above or below the basin so it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them instead.
+% The goal of this experiment is to mimic a typical person with healthy eyesight's search behaviour. 
+% In such a scenario, a person would see the objects currently within their field of view and use their prior knowledge and intuition to make a decision on where to look next.
+% For example, a person in bathroom facing the basin after washing their hands is unlikely to find a hand dryer placed above or below the basin so it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them instead.
 
@@
 It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
-In this case, the human acts as both the controller and actuator. 
-The app only reads out the objects upon the user's request by tapping on the screen. 
+In this case, the human acts as both the controller and the actuator. 
+Similarly to other commercially available applications \tofix{add references to VizWiz, seeingAI, taptapsee}, the unguided version of our app only reads out the objects upon the user's request by tapping on the screen.
 When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.
 
-To mimic the normal search behaviour and allow the participant's to use their intuition and prior knowledge, we ignored the learning effect for this experiment and verbally informed them what their target was for each experiment run.
+% To mimic the normal search behaviour and allow the participant's to use their intuition and prior knowledge, we ignored the learning effect for this experiment and verbally informed them what their target was for each experiment run.
 
@@
 
-In this experiment, we evaluate the performance of the guidance system in an object search task, where the perception and control tasks are performed by the guidance system and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor.
-This is modelled in the schematic in Fig.~\ref{fig:sys-diagram}.
-
-The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object faster themselves.
-This also isolated the performance measurement to the guidance system alone.
-An experiment run started with the experiment staff selecting the target.
+In this experiment, we evaluate the performance of the guidance system in an object search task, where the perception and control tasks are performed by the guidance system and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor (see Fig.~\ref{fig:sys-diagram}).
+%
+To reduce the possibility of the participants ignoring the guidance instructions to find the target object by themselves, they were not told which objects they were actually looking for.
+This also helped to focus on the performance measurement of the guidance system only, isolating it from external factors such as user commonsense or other biases.
+A new run then started with the experiment staff selecting the (unknown) target object for the user.
 

### 2019-07-05 paper.tex

@@
 
-The target acquisition rate (TAR) is the proportion of objects the participants found during an experiment. 
-For example, a TAR of 0.5 indicates that a participant found the target object in 50\% of searches. 
-Taking each participant's TAR as a datum, we found the unguided case produced a higher average TAR (0.54 vs. 0.46), meaning that participants found 8\% more objects without guidance instructions.
-However, the Kruskal-Wallis (KW) test for non-normal data shows that these results are statistically not significantly different ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR.
+As in~\cite{lock2019active}, we use the target acquisition rate (TAR) to compute the proportion of objects that the participants found during an experiment. 
+For example, a TAR of 0.5 indicates that a participant found the target object in 50\% of the searches. 
+Taking each participant's TAR as a datum, the unguided case produced a higher average TAR (0.54 vs. 0.46), meaning that the participants found 8\% more objects without guidance instructions.
+However, the Kruskal-Wallis (KW) test for non-normal data shows that statistically there is no significant difference between these results ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR.
 All the experiment results are summarised in Table~\ref{tab:results}.
@@
 The time it takes to find a target object is an important indicator of system performance, where less time indicates a shorter search time and increased performance.
-The data for the search times for each experiment are shown in Fig.~\ref{fig:boxplots}.
+The data for the search times in the guided and unguided experiments are shown in Fig.~\ref{fig:boxplots}.
+%
+It can be seen that the guidance system reduced the overall time to find each target object.
+This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
+These results compare also favourably with those obtained in our previous version of the system~\cite{lock2019active}, where an average time-to-target of 31s was recorded.
+\tofix{Where did you get 31s?
+The VISAPP paper says 34s, although the average on table 2 of that paper is 32.3s.
+Which one is the right number?}
+However, it should be noted that the system implementation and experimental design in the current paper are significantly different from our previous work, so this comparison is interesting but not indicative of any major improvement.
+% \todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}
 
@@
   \includegraphics[width=1.0\textwidth]{figures/boxplot_combined.png}
-  \caption{A set of boxplots comparing the total linear and angular displacements, as well as the time to target for each experiment. }\label{fig:boxplots}
+  \caption{A set of boxplots comparing the total linear and angular displacements, as well as the time to target for each experiment.
+\tofix{can you swap ang-displacement and time-to-target plots?} }\label{fig:boxplots}
 \end{figure}
-
-From Fig.~\ref{fig:boxplots}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
-This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
-These results compare favourably with those collected from experiments performed with this system's previous iteration where an average time to target of 31s was recorded~\cite{lock2019active}. 
-However, it should be noted that the system implementation and experiment design for this work is significantly different and this comparison is symbolic more than it is indicative of major improvement.
-\todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}
 
@@
 
-To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
+Finally, to give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
 In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user.
-
+%
 The device displacement was measured in both linear ($x, y, z$) and angular (pan, tilt) dimensions.
@@
 
-The boxplots for the total angle displacement show a consistent reduction in radians for the guided case for both the pan (\SI{0.68}{\radian} vs.
+The boxplots for the total angular displacement show a consistent reduction in radians in the guided case for both the pan (\SI{0.68}{\radian} vs.
 \SI{0.99}{\radian}, $p_{kw}=0.029$) and tilt dimensions (\SI{0.68}{\radian} vs.
 \SI{1.05}{\radian}, $p_{kw}=0.011$).
-The guidance system therefore reduces the total angular displacement to find the objects by 31\% and 35\% for the pan and tilt dimensions respectively. 
+The guidance system therefore reduces the total angular displacement to find the objects by 31\% and 35\% for the pan and tilt dimensions, respectively. 
 The total linear displacement is also reduced when using the guidance interface by approximately 36\% (\SI{0.23}{\metre} vs. \SI{0.36}{\metre}, $p_{kw}=0.012$).
@@
 
-\todo{Make sure paper fits into 10+1 page limit for content and references}
+% \todo{Make sure paper fits into 10+1 page limit for content and references}
 
@@
 
-In this work, we presented ActiVis, a mobile guidance system that uses an object detector to scan the environment for objects and a POMDP-based controller and audio interface to generate and present the user with guidance instructions.
-We implemented this system on an Android app and tested it with a group of 10 participants to evaluate its effectiveness compared to a baseline, unguided case that only uses the object detector and relies on the human to generate the search path.
-The key results from these experiments are that the guidance system improved the participants' target-searching performance, reducing the total search time and overall camera manipulation effort required when compared to a base case.
-However, the participants were able to find 8\% more objects on average in the unguided case, but this result was found to be statistically insignificant. 
-With these results, we can reasonably conclude that our system enables a blind or blindfolded user to find a target object and does so better than the alternative base case.
+In this work, we presented ActiVis, a mobile guidance system to scan the environment for finding objects, which uses a POMDP-based controller and a vision-based object detector, combined with an audio interface, to generate instructions for the user.
+We implemented this system on an Android app and tested it with a group of 10 participants to evaluate its effectiveness compared to an unguided object detector. 
+The key results from these experiments are that the guidance system improved the participants' target-searching performance, reducing the total search time and overall camera manipulation effort required to find an object in an unknown environment.
+% However, the participants were able to find 8\% more objects on average in the unguided case, but this result was found to be statistically insignificant. 
+From these results, we can reasonably conclude that our new active search approach is potentially useful for similar mobile applications to help people with visual impairments.
 

### 2019-07-08 paper.tex
Added more detailed future work to conclusion

@@
   \includegraphics[height=4cm]{figures/object_grid/grid.png}
-  \caption{The system in use during an experiment with a blindfolded participant. \tofix{can you add another image with (most of) the objects? maybe arranged in a grid} }\label{fig:system-in-use}
+  \caption{The system in use during an experiment with a blindfolded participant. }\label{fig:system-in-use}
 \end{figure}
@@
 
-A POMDP model is described by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$ (where $s, s' \in \mathbf{S}$) after executing action $a$ (where $a \in \mathbf{A}$), and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
-$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making observation $o \in \mathbf{\Omega}$ when in state $s$ after executing action $a$.
-\tofix{sure about this?
-I think the observation is before the action...}
-Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards, which affects the model's convergence rate.
+A POMDP model is described by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$ (where $s, s' \in \mathbf{S}$) after executing action $a$ (where $a \in \mathbf{A}$), and $\mathbf{R}$ is the reward the agent receives for executing $a$ and reaching $s'$.
+$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making observation $o \in \mathbf{\Omega}$ when in $s$ after executing $a$.
+Finally, $\mathbf{b}$ is a belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards, which affects the model's convergence rate.
 The POMDP's parameters and training process are discussed next.
@@
 The state is given by $s = \langle u, n, v \rangle$, where $u$ is the object within view, $n$ is the number of search steps taken during the search and $v$ is a binary variable indicating whether a waypoint has been visited or not.
-
 The possible actions that dictates the location where the mobile device will generate the next waypoint are given by $\mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}$.
-
 $\mathbf{T}$ was determined by extracting the inter-object spatial relationships for a limited number of objects, in terms of the actions $\mathbf{A}$, from the OpenImages~\cite{openimages} dataset. 
@@
 The reward values were empirically determined starting from the implementation of our previous MDP model~\cite{lock2019active}, the rewards of which are summarised in Table~\ref{tab:rewards} together with the new ones.
-\tofix{can you explain why the last reward (otherwise) is much bigger than before, even bigger than the -75 rewards?}
+%\tofix{can you explain why the last reward (otherwise) is much bigger than before, even bigger than the -75 rewards?}
+The penalty given for every waypoint generated that does not lead to the target was significantly increased for this model to offset the delay before large penalties are introduced and increase the model's urgency.
 
@@
 $\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector.
-These values were found by performing a set of classification tests with the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$. \tofix{you mean $\mathbf{O}$?}
+These values were found by performing a set of classification tests with the object detector and generating a confusion matrix to populate $\mathbf{O}$.
 
@@
 
-Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects (e.g.
-door, desk).
+Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects (e.g.\ door, desk).
 Also, to minimise any cross-experiment learning effects, two different sets of objects were used for each experiment.
 If any (medium-small) objects occurred in both experiments, they were placed at different positions.
-In particular, the objects in the guided case experiment are $\mathbf{U}_{g} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided case are $\mathbf{U}_{ng} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.
+In particular, the objects in the guided case experiment are $\mathbf{U}_{g} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided case are $\mathbf{U}_{ug} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.
 
@@
 A time limit of 45 seconds was set for each experiment run, which ended either by finding the target object or reaching the time limit.
-There was one experiment run per target in the respective environment. \tofix{not clear here: how many object searches were done by each participant in the guided and unguided cases?}
+There was one experiment run per target in each respective environment, giving 8 experiment runs for each the guided and unguided cases.
+%\tofix{not clear here: how many object searches were done by each participant in the guided and unguided cases?}
 
@@
 In this case, the human acts as both the controller and the actuator. 
-Similarly to other commercially available applications \tofix{add references to VizWiz, seeingAI, taptapsee}, the unguided version of our app only reads out the objects upon the user's request by tapping on the screen.
+Similar to other commercially available applications, such as SeeingAI\footnote{apps.apple.com/us/app/seeing-ai/id999062298} and TapTapSee\footnote{play.google.com/store/apps/details?id=com.msearcher.taptapsee.android}, the unguided version of our app only reads out the objects upon the user's request by tapping on the screen.
 When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.
@@
 Taking each participant's TAR as a datum, the unguided case produced a higher average TAR (0.54 vs. 0.46), meaning that the participants found 8\% more objects without guidance instructions.
-However, the Kruskal-Wallis (KW) test for non-normal data shows that statistically there is no significant difference between these results ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR.
+However, the Kruskal-Wallis (KW) test for non-normal data shows that statistically there is no significant difference between these results ($p_{kw} = 0.16$), meaning we cannot conclude which experiment produced the best TAR.\
 All the experiment results are summarised in Table~\ref{tab:results}.
@@
 This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
-These results compare also favourably with those obtained in our previous version of the system~\cite{lock2019active}, where an average time-to-target of 31s was recorded.
-\tofix{Where did you get 31s?
+These results compare also favourably with those obtained in our previous version of the system~\cite{lock2019active}, where an average time-to-target of 34s was recorded.%\tofix{Where did you get 31s?
 The VISAPP paper says 34s, although the average on table 2 of that paper is 32.3s.
@@
   \includegraphics[width=1.0\textwidth]{figures/boxplot_combined.png}
-  \caption{A set of boxplots comparing the total linear and angular displacements, as well as the time to target for each experiment.
-\tofix{can you swap ang-displacement and time-to-target plots?} }\label{fig:boxplots}
+  \caption{A set of boxplots comparing the total linear and angular displacements, as well as the time to target for each experiment.}\label{fig:boxplots}
 \end{figure}
@@
 
-The next steps for the project are to refine and expand the object detector to include objects from other environments.
+The system can benefit from future work that focuses on improving the flexibility and usability of the system. 
+Using a dataset specifically designed for active vision tasks that include the absolute positions of objects as well as the camera in a diverse set of real scenes, will make it possible to extend the POMDP model into 3 dimensions and use more accurate transition and observation functions.
+The University of North Carolina's Active Vision Dataset\cite{active2017dataset} has a limited set of object and scene classes, but is a step in the right direction.
+The usability of the system can potentially be improved by replacing the simple sine-wave tone with a richer and more pleasant tone, such as musical instruments, and allow for the parameters that control the interface's behaviour adapt to the user over time.
+%Furthermore, such a dataset will make it possible to replace the relational transition and observation functions used in this work, with more realistic ones that will allow a wider set of actions to be used.
+
+%The next steps for the project are to refine and expand the object detector to include objects from other environments.
 \tofix{that's it?
@@
 This research is partly supported by a Google Faculty Research Award (Winter 2015).
-\tofix{any charity directly involved in the experiments?}
+We would like to thank the Voluntary Centre Services UK for their help in facilitating the experiments with people with limited vision. 
+%\tofix{any charity directly involved in the experiments?}
 
-\tofix{check all references to use correct information and full list of authors (suggest to use manual input on tools like JabRef)}
+%\tofix{check all references to use correct information and full list of authors (suggest to use manual input on tools like JabRef)}
 \bibliographystyle{splncs04}

### 2019-07-08 paper.tex
Re-read and review of content. Fixed all outstanding comments

@@
 This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, $e$, and drive the output to some reference, $r$.
-In our case, the system incorporates a human within the loop; $r$ is the target object and $y$ is the actual observation of the mobile phone's camera.
+In our case, the system incorporates a human within the loop; $r$ is the target object and $y$ is the actual observation of the mobile device's camera.
 
@@
 
-Adding a human into the loop means to have an additional block, $H$, representing a human that receives a control signal, $u$, from the controller, $K$. 
-However, the challenge is that a person may interpret $u$ in some unpredictable way, resulting in the signal $u*$ that points the camera, $P$, to a new object observation,~$y$.
-It is therefore important to design $K$ to be robust enough to accommodate different user habits and limitations, ensuring that $u*$ tracks $u$ as closely as possible. 
-The object detector's classification errors, $n$, is added to the feedback loop as a noise signal that affects $K$'s output.
+Adding a human into the loop requires an additional block, $H$, representing a human that receives a control signal, $u$, from the controller, $K$. 
+However, the challenge is that a person may interpret $u$ in some unpredictable way, resulting in the signal $u^*$ that points the camera, $P$, to a new object observation,~$y$.
+It is therefore important to design $K$ to be robust enough to accommodate different user habits and limitations, to ensure that $u^*$ tracks $u$ as closely as possible. 
+The object detector's classification error, $n$, is added to the feedback loop as a noise signal that affects $K$'s output.
 
-In our previous work~\cite{lock2019active}, we assumed a perfect object classifier and solved the problem using an MDP.
-In this paper we remove that assumption and replace the MDP with a POMDP-based controller that can handle uncertainties in the object detection and classification. 
+In our previous work~\cite{lock2019active}, we assumed a perfect object classifier and solved the problem using an MDP.\
+In this paper we remove that assumption and replace the MDP with a POMDP-based controller that can handle uncertainties in the object detection and classification output. 
 Our new controller works by generating a trail of virtual waypoints for the user to point the camera towards, which eventually leads to the target object.
 The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
-The design and implementation of this controller are discussed next.
+%The design and implementation of this controller are discussed next.
 
@@
 
-A POMDP is an extension of the MDP that handles cases where the state is not directly observable, allowing it to be used in more realistic scenarios. 
-The implication of this is that a POMDP-based agent does not know its state at any point in time, but must infer it based on the known model parameters and sensor accuracy, which in our case is the object detector's accuracy.
+A POMDP is an extension to a MDP that handles cases where the state is not directly observable, allowing it to be used in more realistic scenarios. 
+The implication, however, is that a POMDP-based agent does not know its state at any point in time, but must infer it based on the known model parameters and sensor accuracy, which in our case is the object detector's accuracy.
 This state inference relies on a so-called {\em belief meta-state}, which is updated with additional observations to reflect the likelihood that the agent is in any given state.
-The belief state is fully observable by the agent and can be used to infer the mobile device's current state and generate the next action.
+The belief state is fully observable by the agent and is used to infer the mobile device's current state and generate the next action.
 
@@
 $\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making observation $o \in \mathbf{\Omega}$ when in $s$ after executing $a$.
-Finally, $\mathbf{b}$ is a belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards, which affects the model's convergence rate.
-The POMDP's parameters and training process are discussed next.
+Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards, which affects the model's convergence rate.
+%The POMDP's parameters and training process are discussed next.
 
@@
 
-The state is given by $s = \langle u, n, v \rangle$, where $u$ is the object within view, $n$ is the number of search steps taken during the search and $v$ is a binary variable indicating whether a waypoint has been visited or not.
-The possible actions that dictates the location where the mobile device will generate the next waypoint are given by $\mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}$.
+The state is given by $s = \langle u, n, v \rangle$, where $u$ is the object within view, $n$ is the number of search steps taken during the search and $v$ is a binary variable indicating whether a waypoint has been visited before.
+The possible actions that dictate the location where the mobile device will generate the next waypoint are given by $\mathbf{A} = \{ \textrm{UP, DOWN, LEFT, RIGHT} \}$.
 $\mathbf{T}$ was determined by extracting the inter-object spatial relationships for a limited number of objects, in terms of the actions $\mathbf{A}$, from the OpenImages~\cite{openimages} dataset. 
@@
 Instead, the previous search locations and search time are fully observable, since they can be tracked by the mobile device.
-$\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector.
+$\mathbf{O}$ therefore only contains the classification/misclassification probabilities of the object detector.
 These values were found by performing a set of classification tests with the object detector and generating a confusion matrix to populate $\mathbf{O}$.
@@
 We use non-intrusive bone-conducting headphones to transmit the audio signals to the user without blocking other ambient sounds.
-The app run in real-time on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{http://developers.google.com/ar/}.% and text-to-speech enabled.
+The app runs in real-time on an Asus ZenPhone AR with Android 7.0 and ARCore\footnote{http://developers.google.com/ar/} enabled.
 
@@
 The latter are obtained by discretising the world into a $6\times6$ grid, where each cell represents a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value when visited.
-This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation $o$ is generated by the object detector. 
+This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation $u$ is generated by the object detector. 
 When the device makes a new observation, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
 The controller uses $o$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
-The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.
-an `UP' output would result in a waypoint being placed one grid square above the current view.
-\tofix{double-check all the quantities an definitions in this section (i.e. states, observations, etc.) are correct, because some were a little mixed-up...}
+The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.\ an `UP' output would result in a waypoint being placed one grid square above the current view.
+%\tofix{double-check all the quantities an definitions in this section (i.e. states, observations, etc.) are correct, because some were a little mixed-up...}
 
@@
 A time limit of 45 seconds was set for each experiment run, which ended either by finding the target object or reaching the time limit.
-There was one experiment run per target in each respective environment, giving 8 experiment runs for each the guided and unguided cases.
+There was one experiment run per target in each respective environment, giving 8 experiment runs for each the of guided and unguided cases.
 %\tofix{not clear here: how many object searches were done by each participant in the guided and unguided cases?}
@@
 To reduce the possibility of the participants ignoring the guidance instructions to find the target object by themselves, they were not told which objects they were actually looking for.
-This also helped to focus on the performance measurement of the guidance system only, isolating it from external factors such as user commonsense or other biases.
+This also helped to focus on the performance measurement of the guidance system only, isolating it from external factors such as user common-sense or other biases.
 A new run then started with the experiment staff selecting the (unknown) target object for the user.

### 2019-07-12 paper.tex
some fixes and revision to conclusions

@@
 
-\begin{table}
+\begin{table}[t]
   \centering
@@
 In this case, the human acts as both the controller and the actuator. 
-Similar to other commercially available applications, such as SeeingAI\footnote{apps.apple.com/us/app/seeing-ai/id999062298} and TapTapSee\footnote{play.google.com/store/apps/details?id=com.msearcher.taptapsee.android}, the unguided version of our app only reads out the objects upon the user's request by tapping on the screen.
+Similar to other commercially available applications, such as SeeingAI\footnote{http://www.microsoft.com/en-us/ai/seeing-ai} and TapTapSee\footnote{http://taptapseeapp.com}, the unguided version of our app only reads out the objects upon the user's request by tapping on the screen.
 When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.
@@
 The system can benefit from future work that focuses on improving the flexibility and usability of the system. 
-Using a dataset specifically designed for active vision tasks that include the absolute positions of objects as well as the camera in a diverse set of real scenes, will make it possible to extend the POMDP model into 3 dimensions and use more accurate transition and observation functions.
-The University of North Carolina's Active Vision Dataset\cite{active2017dataset} has a limited set of object and scene classes, but is a step in the right direction.
-The usability of the system can potentially be improved by replacing the simple sine-wave tone with a richer and more pleasant tone, such as musical instruments, and allow for the parameters that control the interface's behaviour adapt to the user over time.
+New datasets that includes the 3D position of objects and camera, similar to what has been done in robotics~\cite{active2017dataset} but with a more diverse set of real scenes, would make it possible to extend our solution training more accurate transition and observation models that can cope with depth.
+The usability of the system can potentially be improved by more sophisticated audio interfaces and creating adaptive control algorithms that change the interface's behaviour based on the user performance over time~\cite{gallina2015}.
 %Furthermore, such a dataset will make it possible to replace the relational transition and observation functions used in this work, with more realistic ones that will allow a wider set of actions to be used.
@@
 \paragraph{{\bf Acknowledgements.}}\label{sec:acknowledge}
-This research is partly supported by a Google Faculty Research Award (Winter 2015).
+This research is partly supported by a Google Faculty Research Award.
 We would like to thank the Voluntary Centre Services UK for their help in facilitating the experiments with people with limited vision. 

### 2019-07-12 paper.tex
Added reference abbreviations, minor stylistic change and edits to fit into 11 pages

@@
 The system can benefit from future work that focuses on improving the flexibility and usability of the system. 
-New datasets that includes the 3D position of objects and camera, similar to what has been done in robotics~\cite{active2017dataset} but with a more diverse set of real scenes, would make it possible to extend our solution training more accurate transition and observation models that can cope with depth.
-The usability of the system can potentially be improved by more sophisticated audio interfaces and creating adaptive control algorithms that change the interface's behaviour based on the user performance over time~\cite{gallina2015}.
+New datasets that include the 3D positions of the objects and camera, similar to what has been done in robotics~\cite{active2017dataset} but with a more diverse set of real scenes, would make it possible to train our model with more accurate transition and observation models and possibly extend it to be able to cope with depth.
+The usability of the system can potentially be improved with a more sophisticated audio interface and adding adaptive control algorithms that change the interface's behaviour based on the user performance over time~\cite{gallina2015}.
 %Furthermore, such a dataset will make it possible to replace the relational transition and observation functions used in this work, with more realistic ones that will allow a wider set of actions to be used.
